### 2012-10-12 paper/paper.tex
paper commit

%\documentclass[11pt,letterpaper,onecolumn]{article}
\documentclass{llncs}
\usepackage{llncsdoc}
%\usepackage[left=1in,top=1in,right=1in,bottom=1in,nohead]{geometry}

\usepackage{epsfig}
\usepackage{times}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{ltxtable}
\usepackage{tabularx}
\usepackage{hhline}
\usepackage{color,colortbl}
\usepackage{url}
\usepackage{boxedminipage}
\usepackage{hyperref}
\usepackage{breakurl}
\usepackage{comment}
%\usepackage{fullpage}

\newcommand\T{\rule{0pt}{2.6ex}}
\newcommand\B{\rule[-1.2ex]{0pt}{0pt}}
\begin{document}

\title{Contextual Identity: A Framework for Usable Privacy}

%\author{Monica Chew,Sid Stamm\\
%\email{\{mmc,sid\}@mozilla.com}}
%\institute{Mozilla}
\maketitle
\section{Introduction}
\begin{quote}I am large, I contain multitudes. --- Walt Whitman,
\begin{em}Song of Myself\end{em} \end{quote}

People reveal different aspects of themselves depending on context. At any
given time, they may be acting as a friend, relative, spouse, co-worker,
acquaintance, or stranger. This observation is not new; Erving Goffman called
this impression management, and Carl Jung called it persona
theory~\cite{goffman,jung}. In this short paper, we call it contextual identity.
%identity as social construct?

Helen Nissenbaum has long argued that privacy violations come not from the
simple sharing of personal information, but rather from sharing that
information in a way that violates social norms, or in the wrong
context~\cite{nissenbaum}. The desire for spontaneous, positive human
interaction often necessitates sharing personal information. Take, for example,
PatientsLikeMe~\cite{patientslikeme}. This site functions as a support group
and also a place for people to share health information, such as drug regimens,
treatment history, side-effects, and more. Though this information is
traditionally considered extremely sensitive, the users of this site clearly
consider the benefits of sharing (longitudinal graphs of their own health
history, building community with people who share their disease) to outweigh
the privacy risks. So long as the contextual integrity of the shared data is
kept intact, users will continue to trust and use the site. Selling user data
intended for one purpose for another (e.g., to insurance companies to discover
uninsurable patients) would be a clear violation of that expectation.
%this story is a positive story to shock security folk with the breadth and
%depth of personal information that ordinary users will share
% instead we could lead with a shocking, negative story like how gay youth get
% killed when they're outed

In offline environments, managing contextual identities is more intuitive than
in online environments. There are cues to help you determine where you are,
who your intended audience is, how many people will overhear you, and how
likely your information is to be re-broadcast in a different context. It is
also true that in offline environments, humans don't have perfect memories and
will eventually what forget.  However, with the advent of increasingly vast
searching, indexing, and archiving cabilities, one cannot rely on forgetting in
online enviroments~\cite{delete}. Thus, managing contextual identities in
online environments has become increasingly difficult and fraught with
mistakes.

One possible solution to this problem is never to post personal information
online, or at least to consider the entire world might be the audience.
However, this solution defies human nature. Given that there are 1 billion
active Facebook users and that 30-40\% of spoken communication is devoted to
informing others about ourselves, humans are bound to fall short of these
guidelines~\cite{tamir,fbusers}. The security and privacy community should
recognize this and develop techniques to meet users' needs rather than
expecting human nature to change.

We attempt to formalize the notion of contextual identity, use it as a
framework to understand existing privacy violations, and propose mitigations to
those violations.

\section{Definitions}
Let
\begin{itemize}
\item $R$ be a set of actors and their relationships to the user
\item $T$ be a set of tasks and their side-effects when performed in service of
$R$
\item $P$ an impression that actors in $R$ have of the user when performing tasks in $T$
\end{itemize}
Let a \textbf{contextual identity} $I$ be a loose coupling of $(R, T, P)$.
A user may have multiple of these. These identities change over time, as users
form and dissolve relationships, and focus on different sets of tasks. The
desirable outcome is that the user can accomplish tasks in $T$ while being able
to predict $R$ and $P$.
%predict rather than "control" is deliberate, since a user can't realistically
%expect to engage in behavior that violates social norms and give whatever
%impression they want

This definition focusses on relationships because most privacy concerns stem
from causing problems with people the users knows~\cite{wang}. This definition
focusses on tasks because users are task-oriented, and it is easy to map user
actions (page navigation, sending email, posting, filling forms) to tasks.
(include?) The definitions of $R$ and $P$ are deliberately underspecified, as
this is work in progress.

\section{Previous work}

Many authors have discovered attacks to link different contextual identities to
the same person. Narayanan and Shmatikov present a re-identification technique
to merge anonymized social graphs from different networks and prove that
Netflix and IMDB and Flickr and Twitter can be
linked~\cite{narayanan1,narayanan2}. Lindamood et al.~and Mislove et al.~show
how to infer previously undisclosed information from released social networking
data~\cite{lindamood,mislove}.

Many authors have noted how re-broadcasting information information out of
context and making information discoverable can lead to user distress (even if
the information was previously public, but not easily
discoverable)~\cite{boyd1,chew,nissenbaum}.

Barth et al.~ provide a formal model for contextual integrity of user
data~\cite{barth}. In contrast to this work, the contextual integrity model
focusses on data as principal rather than users.

\begin{comment}TODO: figure out how to cite this. Why is this short
paper's model worth pursuing? It's simpler, and focusses on the user rather
than data.
\end{comment}

Although network attacks are very powerful, at the current time they require a
level of expertise and resources not typically held by those causing the most
worry to users. A brief survey of social networking advice reveals that the
major causes of concern come not from a dedicated graph expert, but people that
the user knows: friends, family, and co-workers~\cite{fbtips2,fbtips1}.
Surveys conducted by Wang et al.~show that typical regrets from posting on
Facebook stem almost exclusively from fear of negative interactions with people
that the users knows~\cite{wang}. The consequences of these negative
interactions can lead to loss of employment or breaking personal relationships.
By contrast, much privacy research has focussed on network privacy, where the
bad actor is a behavioral tracking service, or a state agent.

\section{Contextual identity violations}
\label{sec:examples}
\subsection{Redistributing information out of context}
Re-distributing information out of its original context often leads to
embarrassment~\cite{nissenbaum}.  In November 2007, Facebook Beacon allowed
third-party sites to publish purchases, travel bookings, movie rentals to the
user's activity stream.  Because of poor opt-out and lack of visibility into
what was being published, user outcry was immediate~\cite{mccarthy,nakashima}.
In December 2007, Google Reader exposed RSS feeds of user-marked news stories
to the user's Google Talk contacts\footnote{Google Talk contacts are everyone
with whom a user has chatted, which might include co-workers, supervisors, and
friends}. Although this feed was always public, prior to this launch it was not
discoverable, leading to a bad experience for many users~\cite{helft}. In
September 2012, Facebook imported old wall posts from 2008 into the new
Timeline interface.  Although wall posts were always visible from profile
pages, the new Timeline interface brought old wall posts (which users used to
treat as private messages, before the advent of ``Like'' and comment buttons)
to the attention of an audience that the user never intended~\cite{timeline}.

In all these examples, the audience $R$ of the identity expanded without user
intervention.

\subsection{Unsatisfiable policies}
Sometimes service providers have policies which preclude isolating multiple
identites. For example, Facebook and Google have a ``Real Names'' policy, which
requires users to register for accounts with their legal
name~\cite{fb_names,google_names}.  These policies presume the users can be one
person to everyone. These policies ignore that community-building happens in
many different contexts, that users have many legitimate reasons for presenting
different identities in different contexts, and that users don't necessarily
want those identities to be linked. For example, disallowing avatar handles as
a primary identifier makes building a gaming community difficult at best, and
linking a gaming identity to a professional identity has already caused
problems for one exposed has already caused problems for Maine Senate candidate
and World of Warcraft gamer Colleen Lachowicz in 2012~\cite{maine}.

It is impossible for users who want to isolate multiple contextual identities
to participate in these networks without violating the terms of service.

\subsection{Federated login}
Facebook Connect is a login platform that allows third-party websites to
authenticate users using their Facebook identity~\cite{fb_connect}. Because it
is against the terms of service to have multiple Facebook accounts, using
Facebook Connect has the unwanted side-effect of linking multiple contextual
identities.

Other login platforms and protocols, including OAuth and BrowserID
do not suffer from this policy or design error~\cite{browserid,oauth}.
\begin{comment}
(TODO:
this is actually kinda complicated -- yahoo, twitter, google allow multiple
accounts but the multi-login support is broken at google, not sure how it is
with others, oauth protocol supports multiple accounts, persona clearly
supports multiple accounts)
\end{comment}

\subsection{User interface errors}
Even in the absence of changes made by service providers to re-contextualize
personal information, it is all too easy for users to broadcast information to
an unintended audience. This phenomenon is so common on Twitter that it has its
own name, ``DM fail'', or Direct Message fail: when the user posts a public
message instead of a private, direct message. Representative Anthony Weiner was
a victim of this mistake when he inadvertently sent compromising pictures of
himself publicly~\cite{weiner}. Considering that this mistake requires
mistyping a single character (\texttt{@} instead of \texttt{d}), it's no
surprise that DM failures are exceedingly common.

Similar to DM failures, posting to the wrong account is also a common mistake.
Because many jobs require posting on social networks on behalf of the company,
many people now have multiple accounts for personal and business use.
KitchenAid, Chrysler, and Google are just three examples whose employees have
made this mistake in the past year~\cite{kitchenaid,chrysler,yegge}.

\subsection{Third party tracking}
\label{sec:tracking}
Even if a user does not participate in social networks, they are still subject
to tracking by virtue of browsing the web. Third-party cookies, flash cookies,
web bugs, device fingerprinting, geolocation, history sniffing and more are
techniques that a dedicated third party could use to collect browsing history
and link contextual identities.

\section{Possible mitigations}

\subsection{Inferring contextual identities}
Accurately detecting the user's current contextual identity, whether
heuristically or through asking the user, is paramount to helping the user
manage it.

Although a person's contextual identities may be subconsciously clear,
expecting users to enumerate their identities and manually curate them is
probably too burdensome. Firefox has a Profile Manager, but not many people
know about it or how to use it, to the extent that it will be
removed\footnote{See \url{https://bugzilla.mozilla.org/show\_bug.cgi?id=214675\#c53}}.

Tang et al.~show that most people do not take the time to create labels and
maintain friend lists~\cite{tang}. However, the same authors show how to use
heterogenous networks to infer relationship types (e.g., manager-subordinate)
through the graph itself is unlabeled.

It may also be possible to infer tasks from the user's activity. For example,
the \texttt{about:profile} Firefox extension uses the Open Directory Project
and Alexa to categorize URLs that the user has visited~\cite{aboutprofile}.

\subsection{Automatic mitigations for information leakage}
Given the set of relationships $R$ and tasks $T$, we can categorize a user's
contextual identities and prevent information leakage between them.  For
example, preventing third-party cookies from being read and set across task
boundaries means that targeted ads for dating would not follow the user when
visiting a technology news site. Knowing the user's current contextual identity
also allows the browser to suppress URL bar suggestions that aren't relevant to
that identity, protecting the user from both shoulder-surfing and distraction.

Privacy modes in Firefox, Chrome, Safari, and Opera are a good first step, but
are no means a complete solution~\cite{ABBJ10}. There is no standard behavior
for private browsing mode, and thus interaction with extensions, treatment of
cookies, history, and bookmarks upon entering and exiting this mode are
different and serve different use cases. Depending on user desire, $R$ when
using private browsing mode may be other household members, or it may be a
service to which the user wants to limit cookie leakage. Another deficit is
that private browsing mode does not adequately serve long-term tasks (such as
curating a set of adult entertainment sites) in any major browser.

Another good partial solution is to prompt the user when they're about to link
multiple contextual identities through a federated login service. For example,
Persona is the suite of tools that implements the BrowserID protocol, and it
supports multiple email identifiers~\cite{browserid}. In this case, when the
user decides to register for a service using Persona, the task $T$ they are
performing is authentication, the relationships $R$ are ones they will engage
in when using the service, and $P$ is tied to the email identifier they use to
register for the service. Because we can categorize the type of service by URL
as \texttt{aboutprofile} does, Persona could prompt the user when they're about
to link the same email identifier to radically different contextual identities,
such as ones for dating and professional use.

\begin{comment}
TODO: Discuss how private browsing mode maps to R, T, P?

At home use case:
R is household
T is porn?
P is null

Searching use case:
R is Google
T is search
P is null

GoogleShring use case
R is Google and the GoogleSharing proxy
T is search or browsing (analytics) (can't use any services that require logon)
P is random
\end{comment}

\subsection{Recovering from mistakes}
\subsubsection{Auditing}
A major cause of user embarrassment is exposing information to the wrong
audience, as illustrated in section~\ref{sec:examples}. A browser is in the
perfect position to intermediate social network posts, aggregate them locally,
and present them to the user when they desire to audit their digital footprint.
For example, a user could see all of the comments and posts they made in the
last week and redact content that is sensitive or too negative, topics that are
frequently regretted~\cite{wang}. Although this approach does not help when the
service provider decides to change the audience on the user's behalf, auditing
gives the user a good opportunity to review posts that might cause
regrets. In the case of high-volume users, such a tool could even incorporate
sentiment analysis to aid the user in finding particularly problematic content.

Profiles can be generated by user-supplied application-level data, but also
implicitly through browsing via techniques in~\ref{sec:tracking}. Collusion is a
tool for visualizing cookies~\cite{collusion}, in particular the third-party
cookies set by tracking sites which are typically ad networks.  Once the user
knows which sites are tracking them, they can choose to block cookies from
those sites.

\subsubsection{Remembering to forget}
Humans don't have perfect memories, and neither should social
networks~\cite{delete}. Many users already engage in manual auditing and
deletion of old posts~\cite{fbtips2}. A better solution would be to build tools
that let the user manage this more easily. Both Twitter and Facebook provide
APIs for deletion\footnote{At the time of this writing, Google Plus offers a
read-only API}. One way to reduce the likelihood of linked contextual
identities would be to provide applications that expire posts after some time.

\begin{comment}
\cite{viegas}blogger's expectation of privacy
\end{comment}

\subsection{Preventing mistakes}
\subsubsection{Slowing information flow}
Sometimes a user might want to prevent mistakes from being made in the first
place. If a user is concerned about a particular service provider, they can
install an extension like Disconnect to disallow cookies from that provider
unless they explicitly want to interact with that site~\cite{disconnect}.

Protocols like Do Not Track are also a good first step to solving this
problem~\cite{dnt}. Although Do Not Track is unenforceable from the client
side, it provides a clear signal to service providers and ad networks
that the user does not want to be tracked. As adoption increases, ignoring this
signal will lead to loss of reputation for service providers that explicitly
act against their users' wishes.

\subsubsection{Visual reminders of context}
To mitigate privacy violations caused by poor user interfaces, the onus must be
on software developers to provide sufficient visual cues of context. For
example, many but not all Google products support multiple accounts. However,
the visual cue to indicate which account is active is a small, easy to ignore
text name at the top right of the page.

Much work has been done for visual verification of domain authenticity in the
context of phishing, but not much has been done for visual verification of
which user credentials are active~\cite{skins}.

\begin{comment}
first party regrets, third party regrets
impossible to judge how big friends of friends
\end{comment}

\section{Open problems}
The mitigations proposed in this work become more complex in the face of shared
devices and overlapping identities. There are good reasons to want to intermix
work and personal identities (increased exposure, serendipitous connections)
and so many people use the same account for both personal and work reasons.

Mobile growth is driving most internet growth, and much of that growth comes
developing countries. The literature on how device sharing works in those
markets is completely lacking. Managing contextual identities on shared devices
promises to be a difficult problem.

\section{Discussion}
People have multiple contextual identities. Sharing personal information in
those contexts is a great way to foster postive human interaction.  We hope
that contextual identity will serve as a framework for both developers to
understand their users' privacy needs, and to develop tools that allow users to
act in their contextual identities in a spontaneous, relaxed, and interesting
way.

\begin{comment}
papers:
expectation of privacy\cite{viegas}
http://jcmc.indiana.edu/vol10/issue3/viegas.html

danah boyd
making sense of privacy and publicity: whose voice counts? does your child's
teacher have a right to be public in her other roles online? does she have a
right to be secular? religious? friend? lover? if you work for company X and
you disagree with their policies, are you allowed to be public about
that:?\cite{boyd2}

close to you “stranger on a train” “stranger on a plane”
\end{comment}

\begin{comment}
\section{Acknowledgements}
The authors thank
Ben Adida
Ed Lee
Lucas Adamski
Mike Connor

\end{comment}

\bibliographystyle{plain}
\bibliography{paper}
\end{document}

### 2012-10-12 paper.tex
added buzz citation, expanded on contextual integrity ref

--- 2012-10-12 paper/paper.tex
@@
 
-Barth et al.~ provide a formal model for contextual integrity of user
-data~\cite{barth}. In contrast to this work, the contextual integrity model
-focusses on data as principal rather than users.
+Barth et al.~provide a formal model for contextual integrity of user
+data~\cite{barth}. The contextual integrity model focusses on the flow of
+personal information in terms of knowledge states held by agents rather than on
+user identity, and works well for modeling privacy legislation and policy. In
+contrast, this work's model provides a framework to understand users' ability
+to represent which identity they want to use depending on context, and works
+well for modeling software features.
 
@@
 discoverable, leading to a bad experience for many users~\cite{helft}. In
-September 2012, Facebook imported old wall posts from 2008 into the new
-Timeline interface.  Although wall posts were always visible from profile
-pages, the new Timeline interface brought old wall posts (which users used to
-treat as private messages, before the advent of ``Like'' and comment buttons)
-to the attention of an audience that the user never intended~\cite{timeline}.
+February 2010, Google Buzz launched, a product that
+exposed the user's most frequent Gmail and Google Talk contacts and their
+publicly available (through previously less discoverable) news and photos.  The
+combination of exposing contacts (which could include abusive ex-husbands,
+co-workers, and friends), as well as aggressively linking photos and news
+items, resulted in a huge backlash~\cite{fugitivus,buzz}. In September 2012,
+Facebook imported old wall posts from 2008 into the new Timeline interface.
+Although wall posts were always visible from profile pages, the new Timeline
+interface brought old wall posts (which users used to treat as private
+messages, before the advent of ``Like'' and comment buttons) to the attention
+of an audience that the user never intended~\cite{timeline}.
 

### 2012-10-12 paper.tex
Updated Definitions section

@@
 \section{Definitions}
-Let
+
+\begin{definition}
+  Given:
   \begin{itemize}
-\item $R$ be a set of actors and their relationships to the user
-\item $T$ be a set of tasks and their side-effects when performed in service of
-$R$
-\item $P$ an impression that actors in $R$ have of the user when performing tasks in $T$
+    \item $R$, a set of actors and their relationships to the user
+    \item $T$, a set of tasks and their side-effects
+    \item $p$, an identity projected by a user or perceived by actors in $R$
   \end{itemize}
-Let a \textbf{contextual identity} $I$ be a loose coupling of $(R, T, P)$.
-A user may have multiple of these. These identities change over time, as users
-form and dissolve relationships, and focus on different sets of tasks. The
-desirable outcome is that the user can accomplish tasks in $T$ while being able
-to predict $R$ and $P$.
-%predict rather than "control" is deliberate, since a user can't realistically
-%expect to engage in behavior that violates social norms and give whatever
-%impression they want
+\medskip
 
-This definition focusses on relationships because most privacy concerns stem
-from causing problems with people the users knows~\cite{wang}. This definition
-focusses on tasks because users are task-oriented, and it is easy to map user
-actions (page navigation, sending email, posting, filling forms) to tasks.
-(include?) The definitions of $R$ and $P$ are deliberately underspecified, as
-this is work in progress.
+  We define a Contextual Identity $I = \{R,T,p\}$, where a user is performing tasks $T$ in view of or interaction with actors in $R$, while representing himself as identity $p$.
+\end{definition}
+
+A user may have multiple contextual identites $I$. These identities change over
+time, as users form and dissolve relationships, and focus on different sets of
+tasks. The user's goal is that the user can accomplish tasks in $T$, interact
+with those in $R$ and claim to be $p$  while being able to predict and assert
+control over as much of $I$ as possible.
+
+Our definition focuses on relationships because most privacy concerns stem
+from causing an unexpected exchange of data with people the users
+knows~\cite{wang}. Tasks are key because users are task-oriented, and it is
+easy to map user actions (page navigation, sending email, posting, filling
+forms) to tasks.  The definition of $R$ is deliberately underspecified, as this
+is work in progress.
+
+\begin{definition}
+  A Contextual Identity Violation occurs when a user's contextual identity parameters $R,T,P$ are controlled by others.
+When a user's tasks are shared with the wrong set $R$, the wrong projected identifier $p$ is employed, or a user is perceivied as undertaking a set of tasks $T$ they do not anticipate, a violation of the integrity of Contextual Identity occurs.
+\end{definition}
+
+Using these definitions, we characterize different types of violation by what part of the contextual identity the user cannot control, and then show how control can be reasserted by a user who employs various mitigation tools.
 

### 2012-10-12 paper.tex
minor text edits to definition section, standardize on lowercase p, use fullpage.sty to get under page limit

@@
 \usepackage{comment}
-%\usepackage{fullpage}
+\usepackage{fullpage}
 
@@
 
-  We define a Contextual Identity $I = \{R,T,p\}$, where a user is performing tasks $T$ in view of or interaction with actors in $R$, while representing himself as identity $p$.
+  We define a Contextual Identity $I = \{R,T,p\}$, where a user performs tasks
+$T$ in view of or interaction with actors in $R$, while representing identity
+$p$.
+
 \end{definition}
 
-A user may have multiple contextual identites $I$. These identities change over
-time, as users form and dissolve relationships, and focus on different sets of
-tasks. The user's goal is that the user can accomplish tasks in $T$, interact
-with those in $R$ and claim to be $p$  while being able to predict and assert
-control over as much of $I$ as possible.
+A user may have multiple contextual identites $\{I\}$. These identities change
+over time, as users form and dissolve relationships, and focus on different
+sets of tasks. The user's goal is to accomplish tasks in $T$,
+interact with those in $R$ and claim to be $p$  while being able to predict and
+assert control over as much of $I$ as possible.
 
@@
 \begin{definition}
-  A Contextual Identity Violation occurs when a user's contextual identity parameters $R,T,P$ are controlled by others.
-When a user's tasks are shared with the wrong set $R$, the wrong projected identifier $p$ is employed, or a user is perceivied as undertaking a set of tasks $T$ they do not anticipate, a violation of the integrity of Contextual Identity occurs.
+  A Contextual Identity Violation occurs when a user's contextual identity
+parameters $R,T,p$ are controlled by others.  When a user's tasks are shared
+with the wrong set $R$, the wrong projected identifier $p$ is employed, or a
+user is perceivied as undertaking a set of tasks $T$ they do not anticipate, a
+violation of the integrity of Contextual Identity occurs.
+
 \end{definition}
@@
 performing is authentication, the relationships $R$ are ones they will engage
-in when using the service, and $P$ is tied to the email identifier they use to
+in when using the service, and $p$ is tied to the email identifier they use to
 register for the service. Because we can categorize the type of service by URL

### 2012-10-13 paper.tex
Squashed commit of the following:
commit 18beeeec53ffb809836818d695e0c8d5ad63e59a
Author: Sid Stamm <sid@mozilla.com>
Date:   Fri Oct 12 17:37:30 2012 -0700

    Added direct use of the formal model.  Also added stuff about google sharing and tor.

@@
 
-We attempt to formalize the notion of contextual identity, use it as a
-framework to understand existing privacy violations, and propose mitigations to
+We provide a simple formalization of the notion of contextual identity, use it as a
+framework to understand existing privacy violations, and analyze mitigations to
 those violations.
+
+\section{Related Work}
+
+Many authors have discovered attacks to link different contextual identities to
+the same person. Narayanan and Shmatikov present a re-identification technique
+to merge anonymized social graphs from different networks and prove that
+Netflix and IMDB and Flickr and Twitter can be
+linked~\cite{narayanan1,narayanan2}. Lindamood et al.~and Mislove et al.~show
+how to infer previously undisclosed information from released social networking
+data~\cite{lindamood,mislove}.
+
+Many authors have noted how re-broadcasting information information out of
+context and making information discoverable can lead to user distress (even if
+the information was previously public, but not easily
+discoverable)~\cite{boyd1,chew,nissenbaum}.
+
+Barth et al.~provide a formal model for contextual integrity of user
+data~\cite{barth}. The contextual integrity model focuses on the flow of
+personal information in terms of knowledge states held by agents rather than on
+user identity, and works well for modeling privacy legislation and policy. In
+contrast, this work's model provides a simple framework to understand users' ability
+to represent which identity they want to project depending on context, and works
+well for modeling how software features affect users' ability to assert choice
+and control.
+
+\begin{comment}TODO: figure out how to cite this. Why is this short
+paper's model worth pursuing? It's simpler, and focuses on the user rather
+than data.
+\end{comment}
+
+Although network attacks are very powerful, at the current time they require a
+level of expertise and resources not typically held by those causing the most
+worry to users. A brief survey of social networking advice reveals that the
+major causes of concern come not from a dedicated graph expert, but people
+close to the user: friends, family, and co-workers~\cite{fbtips2,fbtips1}.
+Surveys conducted by Wang et al.~show that typical regrets from posting on
+Facebook stem almost exclusively from fear of negative interactions with people
+that the users knows~\cite{wang}. The consequences of these negative
+interactions can lead to loss of employment or breaking personal relationships.
+Most previous privacy research has focused on distant adversaries, where the
+bad actor is a behavioral tracking service, state agent or unknown
+eavesdropper; in contrast, we assert that users care more about their
+interactions with others close to them.
 
@@
 
-\section{Previous work}
-
-Many authors have discovered attacks to link different contextual identities to
-the same person. Narayanan and Shmatikov present a re-identification technique
-to merge anonymized social graphs from different networks and prove that
-Netflix and IMDB and Flickr and Twitter can be
-linked~\cite{narayanan1,narayanan2}. Lindamood et al.~and Mislove et al.~show
-how to infer previously undisclosed information from released social networking
-data~\cite{lindamood,mislove}.
-
-Many authors have noted how re-broadcasting information information out of
-context and making information discoverable can lead to user distress (even if
-the information was previously public, but not easily
-discoverable)~\cite{boyd1,chew,nissenbaum}.
-
-Barth et al.~provide a formal model for contextual integrity of user
-data~\cite{barth}. The contextual integrity model focusses on the flow of
-personal information in terms of knowledge states held by agents rather than on
-user identity, and works well for modeling privacy legislation and policy. In
-contrast, this work's model provides a framework to understand users' ability
-to represent which identity they want to use depending on context, and works
-well for modeling software features.
-
-\begin{comment}TODO: figure out how to cite this. Why is this short
-paper's model worth pursuing? It's simpler, and focusses on the user rather
-than data.
-\end{comment}
-
-Although network attacks are very powerful, at the current time they require a
-level of expertise and resources not typically held by those causing the most
-worry to users. A brief survey of social networking advice reveals that the
-major causes of concern come not from a dedicated graph expert, but people that
-the user knows: friends, family, and co-workers~\cite{fbtips2,fbtips1}.
-Surveys conducted by Wang et al.~show that typical regrets from posting on
-Facebook stem almost exclusively from fear of negative interactions with people
-that the users knows~\cite{wang}. The consequences of these negative
-interactions can lead to loss of employment or breaking personal relationships.
-By contrast, much privacy research has focussed on network privacy, where the
-bad actor is a behavioral tracking service, or a state agent.
-
 \section{Contextual identity violations}
@@
 \subsection{Redistributing information out of context}
+(Lack of control over $R$).\\
 Re-distributing information out of its original context often leads to
@@
 \subsection{Unsatisfiable policies}
+(Lack of control over $p$).\\
 Sometimes service providers have policies which preclude isolating multiple
@@
 It is impossible for users who want to isolate multiple contextual identities
-to participate in these networks without violating the terms of service.
+to participate in these networks without violating the terms of service.  The
+Google ``legal name'' policy prohibits users from asserting control over $p$.
 
 \subsection{Federated login}
+(Lack of flexibility in $p$).\\
 Facebook Connect is a login platform that allows third-party websites to
@@
 
-Other login platforms and protocols, including OAuth and BrowserID
-do not suffer from this policy or design error~\cite{browserid,oauth}.
-\begin{comment}
-(TODO:
+Similar to the Unsatisfiable policies, many federated login systems simply
+don't have the ability to allow users multiple $p$ values, or identifiers.
+Other federated login systems may support and allow multiple identifiers, but
+it can be poorly implemented or difficult to discover, which essentially means
+the feature isn't used.
+There are some login platforms and protocols, including OAuth and BrowserID
+that do not suffer from this policy or design error~\cite{browserid,oauth},
+giving a user better control over which value of $p$ he employs in his
+contextual identity.
+\begin{comment} (TODO:
 this is actually kinda complicated -- yahoo, twitter, google allow multiple
@@
 \subsection{User interface errors}
+(Lack of control over $R$).\\
 Even in the absence of changes made by service providers to re-contextualize
@@
 \label{sec:tracking}
+(Lack of control over $T$, and correlation across values of $p$).\\
 Even if a user does not participate in social networks, they are still subject
@@
 techniques that a dedicated third party could use to collect browsing history
-and link contextual identities.
+and link contextual identities through correlation of tasks in $T$ for various
+identity values $p$.
 
@@
 \subsection{Automatic mitigations for information leakage}
-Given the set of relationships $R$ and tasks $T$, we can categorize a user's
+Given a set of relationships $R$ and tasks $T$, one can categorize a user's
 contextual identities and prevent information leakage between them.  For
@@
 using private browsing mode may be other household members, or it may be a
-service to which the user wants to limit cookie leakage. Another deficit is
-that private browsing mode does not adequately serve long-term tasks (such as
-curating a set of adult entertainment sites) in any major browser.
+service to which the user wants to limit cookie leakage. A strong contextual
+identity mechanism allows users control over $R$ or over $T$ when $R$ is
+clearly identified to them, but the various privacy modes in different web
+browsers either allows the user control over $T$ or over $R$, but not both at
+the same time.
 
-Another good partial solution is to prompt the user when they're about to link
+A partial solution is to prompt the user when they're about to link
 multiple contextual identities through a federated login service. For example,
@@
 to link the same email identifier to radically different contextual identities,
-such as ones for dating and professional use.
+such as ones for dating and professional use.  Persona allows the user direct
+control over $p$ given a context ($R,T$) in which they're authenticating.
 
@@
 
-\subsection{Recovering from mistakes}
+\subsection{Recovering from Mistakes}
 \subsubsection{Auditing}
 A major cause of user embarrassment is exposing information to the wrong
-audience, as illustrated in section~\ref{sec:examples}. A browser is in the
-perfect position to intermediate social network posts, aggregate them locally,
+audience, as illustrated in Section~\ref{sec:examples}. A browser is in an
+ideal position to intermediate social network posts, aggregate them locally,
 and present them to the user when they desire to audit their digital footprint.
+
 For example, a user could see all of the comments and posts they made in the
 last week and redact content that is sensitive or too negative, topics that are
-frequently regretted~\cite{wang}. Although this approach does not help when the
-service provider decides to change the audience on the user's behalf, auditing
-gives the user a good opportunity to review posts that might cause
-regrets. In the case of high-volume users, such a tool could even incorporate
-sentiment analysis to aid the user in finding particularly problematic content.
+frequently regretted~\cite{wang}.  This redacting is equivalent to asserting
+better control over $T$. Although this approach does not help when the service
+provider decides to change the audience on the user's behalf (loss of control
+over $R$), auditing gives the user a good opportunity to review posts that
+might cause regrets. In the case of high-volume users, such a tool could
+incorporate sentiment analysis to aid the user in finding particularly
+problematic content.  This effectively helps users adjust $T$ when $R$ changes
+unexpectedly; while it does not help bring users into better control over $R$,
+it can help them minimize the impact of a changing $R$.
 
 Profiles can be generated by user-supplied application-level data, but also
-implicitly through browsing via techniques in~\ref{sec:tracking}. Collusion is a
+implicitly through browsing via techniques in Section~\ref{sec:tracking}. Collusion is a
 tool for visualizing cookies~\cite{collusion}, in particular the third-party
@@
 knows which sites are tracking them, they can choose to block cookies from
-those sites.
+those sites.  This type of tool allows users good control over $R$ by limiting
+who sees the tracks they create.
 
-\subsubsection{Remembering to forget}
-Humans don't have perfect memories, and neither should social
-networks~\cite{delete}. Many users already engage in manual auditing and
+\subsubsection{Remembering to Forget}
+Humans don't have perfect memories, and one could argue that social
+networks should also forget~\cite{delete}. Many users already engage in manual auditing and
 deletion of old posts~\cite{fbtips2}. A better solution would be to build tools
-that let the user manage this more easily. Both Twitter and Facebook provide
+that let the user manage this more easily through an API: both Twitter and Facebook provide
 APIs for deletion\footnote{At the time of this writing, Google Plus offers a
@@
 identities would be to provide applications that expire posts after some time.
+This would help users better contain the whole context ($R,T$) by segmenting
+one large audience and one large set of tasks into smaller temporal partitions.
 
@@
 
-\subsection{Preventing mistakes}
-\subsubsection{Slowing information flow}
+\subsection{Preventing Mistakes}
+\subsubsection{Controlling Information Flow}
 Sometimes a user might want to prevent mistakes from being made in the first
@@
 unless they explicitly want to interact with that site~\cite{disconnect}.
+This type of tool (cookie blocker) helps users assert control over audience ($R$).
 
@@
 act against their users' wishes.
+This type of tool (cookie blocker) helps users assert control over the effects of their actions ($T$).
+
+The Google Sharing project allows users of Google services to share and mix the way Google identifies them~\cite{googlesharing}.
+The effect is that users employ a contextual identity $\{T_{gs}, R_{gs}, p\}$ with a shared $p$.
+These users employ it only for Google sites ($R_{gs} = Google$) and can accomplish tasks $T_{gs}$ while associating all their actions with a random $p$ also associated with many other users.
+This devalues $p$ and makes it difficult to correlate $T_{gs}$ with $T$ from another of the users' contextual identities.
+
+Channel encryption systems like TOR\footnote{The Onion Router: \url{https://www.torproject.org}} allow the users more network secrecy; this allows them to better control their audience $R$ by hiding their actions from network operators.
 
@@
 The authors thank
+Lucas Adamski
 Ben Adida
+Mike Connor
 Ed Lee
-Lucas Adamski
-Mike Connor
-
 \end{comment}

### 2012-10-13 paper.tex
copy-edited whole thing, added expiring contextual identities section

@@
 context~\cite{nissenbaum}. The desire for spontaneous, positive human
-interaction often necessitates sharing personal information. Take, for example,
+interaction often leads to sharing personal information. For example, take
 PatientsLikeMe~\cite{patientslikeme}. This site functions as a support group
-and also a place for people to share health information, such as drug regimens,
+and as a place for people to share health information, such as drug regimens,
 treatment history, side-effects, and more. Though this information is
 traditionally considered extremely sensitive, the users of this site clearly
-consider the benefits of sharing (longitudinal graphs of their own health
-history, building community with people who share their disease) to outweigh
-the privacy risks. So long as the contextual integrity of the shared data is
-kept intact, users will continue to trust and use the site. Selling user data
-intended for one purpose for another (e.g., to insurance companies to discover
-uninsurable patients) would be a clear violation of that expectation.
+value the benefits of sharing (longitudinal graphs of their own health history,
+building community with people who share their disease). Further, sharing
+personal information does not mean that the users don't value privacy.  Selling
+user data originally intended for one purpose for another (e.g., to insurance
+companies to discover uninsurable patients) would be a gross violation of
+users' privacy expectations.
+
 %this story is a positive story to shock security folk with the breadth and
@@
 will eventually what forget.  However, with the advent of increasingly vast
-searching, indexing, and archiving cabilities, one cannot rely on forgetting in
-online enviroments~\cite{delete}. Thus, managing contextual identities in
-online environments has become increasingly difficult and fraught with
-mistakes.
+searching, indexing, and archiving capabilities, one cannot rely on forgetting
+in online enviroments~\cite{delete}. Thus, managing contextual identities 
+online has become increasingly difficult and fraught with mistakes.
 
@@
 We provide a simple formalization of the notion of contextual identity, use it as a
-framework to understand existing privacy violations, and analyze mitigations to
+framework to understand existing privacy violations, and analyze mitigations of
 those violations.
@@
 to merge anonymized social graphs from different networks and prove that
-Netflix and IMDB and Flickr and Twitter can be
+user identifiers from Netflix and IMDB and Flickr and Twitter can be
 linked~\cite{narayanan1,narayanan2}. Lindamood et al.~and Mislove et al.~show
@@
 
-Although network attacks are very powerful, at the current time they require a
-level of expertise and resources not typically held by those causing the most
-worry to users. A brief survey of social networking advice reveals that the
-major causes of concern come not from a dedicated graph expert, but people
+Although network inference and merging attacks are very powerful, at the
+current time they require a level of expertise and resources not available to
+most people. A brief survey of social networking
+advice reveals that the
+major causes of concern come not from a dedicated social graph expert, but people
 close to the user: friends, family, and co-workers~\cite{fbtips2,fbtips1}.
@@
 Facebook stem almost exclusively from fear of negative interactions with people
-that the users knows~\cite{wang}. The consequences of these negative
+that the user knows~\cite{wang}. The consequences of these negative
 interactions can lead to loss of employment or breaking personal relationships.
@@
 
-A user may have multiple contextual identites $\{I\}$. These identities change
+A user may have multiple contextual identities $\{I\}$. These identities change
 over time, as users form and dissolve relationships, and focus on different
@@
 easy to map user actions (page navigation, sending email, posting, filling
-forms) to tasks.  The definition of $R$ is deliberately underspecified, as this
-is work in progress.
+forms) to tasks.
 
 \begin{definition}
-  A Contextual Identity Violation occurs when a user's contextual identity
+  A Contextual Identity Violation occurs when
 parameters $R,T,p$ are controlled by others.  When a user's tasks are shared
 with the wrong set $R$, the wrong projected identifier $p$ is employed, or a
-user is perceivied as undertaking a set of tasks $T$ they do not anticipate, a
+user is perceived as performing tasks $T$ they do not anticipate, a
 violation of the integrity of Contextual Identity occurs.
@@
 embarrassment~\cite{nissenbaum}.  In November 2007, Facebook Beacon allowed
-third-party sites to publish purchases, travel bookings, movie rentals to the
+third-party sites to publish purchases, travel bookings, movie rentals and more to the
 user's activity stream.  Because of poor opt-out and lack of visibility into
@@
 Although wall posts were always visible from profile pages, the new Timeline
-interface brought old wall posts (which users used to treat as private
-messages, before the advent of ``Like'' and comment buttons) to the attention
-of an audience that the user never intended~\cite{timeline}.
+interface brought old wall posts which users used to treat as private
+messages, before the advent of ``Like'' and comment buttons, to the attention
+of an audience that the user never anticipated~\cite{timeline}.
 
-In all these examples, the audience $R$ of the identity expanded without user
+In all these examples, the audience $R$ of the contextual identity expanded without user
 intervention.
@@
 \subsection{Unsatisfiable policies}
+\label{sec:policies}
 (Lack of control over $p$).\\
-Sometimes service providers have policies which preclude isolating multiple
-identites. For example, Facebook and Google have a ``Real Names'' policy, which
+Some service providers have policies which preclude isolating multiple
+contextual identities. For example, Facebook and Google have a ``Real Names'' policy, which
 requires users to register for accounts with their legal
@@
 want those identities to be linked. For example, disallowing avatar handles as
-a primary identifier makes building a gaming community difficult at best, and
-linking a gaming identity to a professional identity has already caused
-problems for one exposed has already caused problems for Maine Senate candidate
-and World of Warcraft gamer Colleen Lachowicz in 2012~\cite{maine}.
+a primary identifier makes building a gaming community difficult. 
+Linking a gaming identity to a professional identity has already caused
+problems for 2012 Maine Senate candidate
+and World of Warcraft gamer Colleen Lachowicz~\cite{maine}.
 
@@
 to participate in these networks without violating the terms of service.  The
-Google ``legal name'' policy prohibits users from asserting control over $p$.
-
-\subsection{Federated login}
-(Lack of flexibility in $p$).\\
-Facebook Connect is a login platform that allows third-party websites to
-authenticate users using their Facebook identity~\cite{fb_connect}. Because it
-is against the terms of service to have multiple Facebook accounts, using
-Facebook Connect has the unwanted side-effect of linking multiple contextual
-identities.
-
-Similar to the Unsatisfiable policies, many federated login systems simply
-don't have the ability to allow users multiple $p$ values, or identifiers.
-Other federated login systems may support and allow multiple identifiers, but
-it can be poorly implemented or difficult to discover, which essentially means
-the feature isn't used.
-There are some login platforms and protocols, including OAuth and BrowserID
-that do not suffer from this policy or design error~\cite{browserid,oauth},
-giving a user better control over which value of $p$ he employs in his
-contextual identity.
-\begin{comment} (TODO:
-this is actually kinda complicated -- yahoo, twitter, google allow multiple
-accounts but the multi-login support is broken at google, not sure how it is
-with others, oauth protocol supports multiple accounts, persona clearly
-supports multiple accounts)
-\end{comment}
+``Real Names'' policy prohibits users from asserting control over $p$.
 
@@
 Because many jobs require posting on social networks on behalf of the company,
-many people now have multiple accounts for personal and business use.
-KitchenAid, Chrysler, and Google are just three examples whose employees have
+it is common to have multiple accounts for personal and business use.
+KitchenAid, Chrysler, and Google are three companies whose employees have
 made this mistake in the past year~\cite{kitchenaid,chrysler,yegge}.
+
+\subsection{Federated login}
+\label{sec:login}
+(Lack of flexibility in $p$).\\
+Facebook Connect is a login platform that allows third-party websites to
+authenticate users using their Facebook identity~\cite{fb_connect}. Because it
+is against the terms of service to have multiple Facebook accounts, using
+Facebook Connect has the unwanted side-effect of linking multiple contextual
+identities.
+
+Similar to section~\ref{sec:policies}, many federated login systems simply
+don't have the ability to allow users multiple $p$ values, or identifiers.
+Other federated login systems have support for multiple identifiers, but
+this feature can be poorly implemented or difficult to discover, leading to
+low use.
+Some login platforms and protocols, such as OAuth and BrowserID,
+do not suffer from this policy or design error~\cite{browserid,oauth},
+giving a user better control over which value of $p$ to employ.
 
@@
 and link contextual identities through correlation of tasks in $T$ for various
-identity values $p$.
+values of $p$.
 
@@
 manage it.
-
-Although a person's contextual identities may be subconsciously clear,
+Although a user may subconsciously be aware of their contextual identities,
 expecting users to enumerate their identities and manually curate them is
-probably too burdensome. Firefox has a Profile Manager, but not many people
-know about it or how to use it, to the extent that it will be
-removed\footnote{See \url{https://bugzilla.mozilla.org/show\_bug.cgi?id=214675\#c53}}.
+probably too burdensome. Firefox has a Profile Manager, but it is so difficult to use that it will be removed.\footnote{See \url{https://bugzilla.mozilla.org/show\_bug.cgi?id=214675\#c53}}.
 
@@
 heterogenous networks to infer relationship types (e.g., manager-subordinate)
-through the graph itself is unlabeled.
+though the graph itself is unlabeled.
 
@@
 using private browsing mode may be other household members, or it may be a
-service to which the user wants to limit cookie leakage. A strong contextual
-identity mechanism allows users control over $R$ or over $T$ when $R$ is
-clearly identified to them, but the various privacy modes in different web
-browsers either allows the user control over $T$ or over $R$, but not both at
-the same time.
+service to which the user wants to limit cookie leakage.
+%this requires more explanation, omitting for now. A strong contextual
+%identity mechanism allows users control over $R$ or over $T$ when $R$ is
+%clearly identified to them, but the various privacy modes in different web
+%browsers either allows the user control over $T$ or over $R$, but not both at
+%the same time.
 
-A partial solution is to prompt the user when they're about to link
+Another partial solution is to prompt the user when they're about to link
 multiple contextual identities through a federated login service. For example,
@@
 register for the service. Because we can categorize the type of service by URL
-as \texttt{aboutprofile} does, Persona could prompt the user when they're about
+as \texttt{about:profile} does, Persona could prompt the user when they're about
 to link the same email identifier to radically different contextual identities,
 such as ones for dating and professional use.  Persona allows the user direct
-control over $p$ given a context ($R,T$) in which they're authenticating.
+control over $p$ given a context {$R,T$} in which they're authenticating.
 
-\begin{comment}
-TODO: Discuss how private browsing mode maps to R, T, P?
-
-At home use case:
-R is household
-T is porn?
-P is null
-
-Searching use case:
-R is Google
-T is search
-P is null
-
-GoogleShring use case
-R is Google and the GoogleSharing proxy
-T is search or browsing (analytics) (can't use any services that require logon)
-P is random
-\end{comment}
+\subsection{Expiring contextual identities}
+Oftentimes a user may have a long-term task, such as wedding planning or house
+buying, that requires constructing a contextual identity. The tasks associated
+with this identity have an externally imposed deadline and may have long-lived
+side-effects, such as long-term cookies that reveal sensitive information
+(e.g., the neighborhood of the house purchase, income information derived from
+purchases, other demographic data). For contextual identities that have
+outlived their usefulness, users would benefit from destruction of side-effects
+in $T$ such as cookie data.
 
@@
 A major cause of user embarrassment is exposing information to the wrong
-audience, as illustrated in Section~\ref{sec:examples}. A browser is in an
+audience, as illustrated in section~\ref{sec:examples}. A browser is in an
 ideal position to intermediate social network posts, aggregate them locally,
 and present them to the user when they desire to audit their digital footprint.
-
 For example, a user could see all of the comments and posts they made in the
-last week and redact content that is sensitive or too negative, topics that are
-frequently regretted~\cite{wang}.  This redacting is equivalent to asserting
-better control over $T$. Although this approach does not help when the service
+last week and redact content that is sensitive or too negative, a frequent cause
+of regret~\cite{wang}.  Redaction allows the user to assert
+better control over $T$ as well as $p$. Although this approach does not help when the service
 provider decides to change the audience on the user's behalf (loss of control
@@
 problematic content.  This effectively helps users adjust $T$ when $R$ changes
-unexpectedly; while it does not help bring users into better control over $R$,
-it can help them minimize the impact of a changing $R$.
+unexpectedly.
 
@@
 implicitly through browsing via techniques in Section~\ref{sec:tracking}. Collusion is a
-tool for visualizing cookies~\cite{collusion}, in particular the third-party
+tool for visualizing cookies~\cite{collusion}, in particular third-party
 cookies set by tracking sites which are typically ad networks.  Once the user
@@
 those sites.  This type of tool allows users good control over $R$ by limiting
-who sees the tracks they create.
+who sees the side-effects in $T$.
 
 \subsubsection{Remembering to Forget}
-Humans don't have perfect memories, and one could argue that social
-networks should also forget~\cite{delete}. Many users already engage in manual auditing and
+Humans don't have perfect memories, and perhaps social
+networks should not either~\cite{delete}. Many users already engage in manual auditing and
 deletion of old posts~\cite{fbtips2}. A better solution would be to build tools
@@
 read-only API}. One way to reduce the likelihood of linked contextual
-identities would be to provide applications that expire posts after some time.
-This would help users better contain the whole context ($R,T$) by segmenting
-one large audience and one large set of tasks into smaller temporal partitions.
+identities or assert better control over $p$ would be to provide applications that expire posts after some time.
+Deletion ane expiration also reduce $R$ (in the case of public posts) and $T$.
+%This would help users better contain the whole context ($R,T$) by segmenting
+%one large audience and one large set of tasks into smaller temporal partitions.
 
@@
 unless they explicitly want to interact with that site~\cite{disconnect}.
-This type of tool (cookie blocker) helps users assert control over audience ($R$).
+This type of tool (cookie blocker) helps users assert control over audience $R$.
 
@@
 signal will lead to loss of reputation for service providers that explicitly
-act against their users' wishes.
-This type of tool (cookie blocker) helps users assert control over the effects of their actions ($T$).
+act against their users' wishes, helping
+users assert control over the effects of their actions $T$.
 
-The Google Sharing project allows users of Google services to share and mix the way Google identifies them~\cite{googlesharing}.
-The effect is that users employ a contextual identity $\{T_{gs}, R_{gs}, p\}$ with a shared $p$.
-These users employ it only for Google sites ($R_{gs} = Google$) and can accomplish tasks $T_{gs}$ while associating all their actions with a random $p$ also associated with many other users.
-This devalues $p$ and makes it difficult to correlate $T_{gs}$ with $T$ from another of the users' contextual identities.
+The Google Sharing project allows users of Google services to confound the way
+Google identifies them~\cite{googlesharing}.  The effect is that users employ a
+contextual identity with a shared $p$.  These users
+employ it only for Google sites and can accomplish tasks
+while associating all their actions with a random $p$ also associated
+with many other users.  This devalues $p$ and makes it difficult to correlate
+tasks with a particular user.
 
@@
 
-\begin{comment}
-first party regrets, third party regrets
-impossible to judge how big friends of friends
-\end{comment}
+\section{Open problems}
+We are largely ignorant of the ways in which users think about contextual
+identity. Building usable software to manage contextual identity demands
+further research.
 
-\section{Open problems}
 The mitigations proposed in this work become more complex in the face of shared
@@
 close to you “stranger on a train” “stranger on a plane”
+first party regrets, third party regrets
+impossible to judge how big friends of friends
+
 \end{comment}

### 2012-10-13 paper.tex
audited uses of p as identity

@@
 traditionally considered extremely sensitive, the users of this site clearly
-value the benefits of sharing (longitudinal graphs of their own health history,
-building community with people who share their disease). Further, sharing
-personal information does not mean that the users don't value privacy.  Selling
-user data originally intended for one purpose for another (e.g., to insurance
-companies to discover uninsurable patients) would be a gross violation of
-users' privacy expectations.
+value the benefits of sharing: longitudinal graphs of their own health history,
+building community with people who share their disease. Further, sharing
+personal information does not mean that the users don't value
+privacy~\cite{boyd2}. Selling user data originally intended for one purpose for
+another (e.g., to insurance companies to discover uninsurable patients) would
+be a gross violation of users' privacy expectations.
 
@@
 also true that in offline environments, humans don't have perfect memories and
-will eventually what forget.  However, with the advent of increasingly vast
+will eventually forget.  However, with the advent of increasingly vast
 searching, indexing, and archiving capabilities, one cannot rely on forgetting
@@
 
-We provide a simple formalization of the notion of contextual identity, use it as a
-framework to understand existing privacy violations, and analyze mitigations of
-those violations.
+We provide a simple formalization of the notion of contextual identity, use it
+as a framework to understand existing privacy violations, and analyze
+mitigations for those violations.
 
@@
 Many authors have noted how re-broadcasting information information out of
-context and making information discoverable can lead to user distress (even if
+context and making information discoverable can lead to user distress, even if
 the information was previously public, but not easily
-discoverable)~\cite{boyd1,chew,nissenbaum}.
+discoverable~\cite{boyd1,chew,nissenbaum}.
 
@@
 user identity, and works well for modeling privacy legislation and policy. In
-contrast, this work's model provides a simple framework to understand users' ability
-to represent which identity they want to project depending on context, and works
+contrast, this work's model provides a simple framework to understand users'
+ability to represent which contextual identity they want to project, and works
 well for modeling how software features affect users' ability to assert choice
@@
 
-\begin{definition}
-  Given:
+Suppose:
   \begin{itemize}
-    \item $R$, a set of actors and their relationships to the user
-    \item $T$, a set of tasks and their side-effects
-    \item $p$, an identity projected by a user or perceived by actors in $R$
+    \item $R$ is a set of actors and their relationships to the user. $R$ may include people that the user knows, service providers, or network operators.
+    \item $T$ is a set of tasks and their side-effects. Examples of tasks
+include page navigation, posting to social networks and searching. Examples of
+side-effects include cookies, geolocation data and browser history.
+    \item $p$ is an impression that the user wishes to project, or that actors
+in $R$ perceive. $p$ encompasses such prosaic information as email identifiers
+or session identifiers, or such sentiment as ``Alice is awesome!''
   \end{itemize}
-\medskip
 
-  We define a Contextual Identity $I = \{R,T,p\}$, where a user performs tasks
-$T$ in view of or interaction with actors in $R$, while representing identity
+\begin{definition} We define a contextual identity $I = \{R,T,p\}$, where a user performs tasks
+$T$ in view of or interaction with actors in $R$, while projecting impression
 $p$.
-
 \end{definition}
@@
 sets of tasks. The user's goal is to accomplish tasks in $T$,
-interact with those in $R$ and claim to be $p$  while being able to predict and
+interact with those in $R$ and project $p$ while being able to predict and
 assert control over as much of $I$ as possible.
@@
 Our definition focuses on relationships because most privacy concerns stem
-from causing an unexpected exchange of data with people the users
+from causing an unexpected exchange of data with people the user
 knows~\cite{wang}. Tasks are key because users are task-oriented, and it is
@@
 \begin{definition}
-  A Contextual Identity Violation occurs when
-parameters $R,T,p$ are controlled by others.  When a user's tasks are shared
-with the wrong set $R$, the wrong projected identifier $p$ is employed, or a
-user is perceived as performing tasks $T$ they do not anticipate, a
-violation of the integrity of Contextual Identity occurs.
+A contextual identity violation occurs when the user cannot predict or control
+parameters $R,T,p$.
+\end{definition}
+When a user's tasks are shared with the wrong set $R$, the wrong projected
+identifier $p$ is employed, or a user is perceived as performing tasks $T$ they
+do not anticipate, a violation of the integrity of contextual identity occurs.
 
+\begin{definition}
+Linkage of contextual identities occurs when a set of $\{I\}$ is associated
+with the same user.
 \end{definition}
 
-Using these definitions, we characterize different types of violation by what part of the contextual identity the user cannot control, and then show how control can be reasserted by a user who employs various mitigation tools.
+When this linkage happens against the will or without the knowledge of the
+user, a violation of the integrity of contextual identity occurs.
+
+Using these definitions, we characterize different types of violation by what
+part of the contextual identity the user cannot control, and then show how
+control can be reasserted by a user who employs various mitigation tools.
 
@@
 
-In all these examples, the audience $R$ of the contextual identity expanded without user
-intervention.
+In all these examples, the audience $R$ of the contextual identity expanded
+without user intervention.
 
@@
 Linking a gaming identity to a professional identity has already caused
-problems for 2012 Maine Senate candidate
-and World of Warcraft gamer Colleen Lachowicz~\cite{maine}.
+problems for 2012 Maine Senate candidate and World of Warcraft gamer Colleen
+Lachowicz~\cite{maine}.
 
@@
 buying, that requires constructing a contextual identity. The tasks associated
-with this identity have an externally imposed deadline and may have long-lived
+with this identity have an externally imposed end date and may have long-lived
 side-effects, such as long-term cookies that reveal sensitive information
@@
 identities or assert better control over $p$ would be to provide applications that expire posts after some time.
-Deletion ane expiration also reduce $R$ (in the case of public posts) and $T$.
+Deletion and expiration also reduce $R$ especially in the case of public posts
+and $T$.
 %This would help users better contain the whole context ($R,T$) by segmenting
@@
 The Google Sharing project allows users of Google services to confound the way
-Google identifies them~\cite{googlesharing}.  The effect is that users employ a
-contextual identity with a shared $p$.  These users
-employ it only for Google sites and can accomplish tasks
-while associating all their actions with a random $p$ also associated
-with many other users.  This devalues $p$ and makes it difficult to correlate
-tasks with a particular user.
+Google identifies them~\cite{googlesharing}. In this case $R$ contains Google
+and the Google Sharing proxy. The effect is that users employ a contextual
+identity with a shared $p$. These users employ it only for Google sites not
+requiring login and can accomplish tasks while associating all their actions
+with a random $p$ also associated with many other users.  This devalues $p$ and
+makes it difficult for Google to correlate tasks with a particular user.
 

### 2012-10-13 paper.tex
ispell

@@
 searching, indexing, and archiving capabilities, one cannot rely on forgetting
-in online enviroments~\cite{delete}. Thus, managing contextual identities
+in online environments~\cite{delete}. Thus, managing contextual identities
 online has become increasingly difficult and fraught with mistakes.
@@
 maintain friend lists~\cite{tang}. However, the same authors show how to use
-heterogenous networks to infer relationship types (e.g., manager-subordinate)
+heterogeneous networks to infer relationship types (e.g., manager-subordinate)
 though the graph itself is unlabeled.
@@
 People have multiple contextual identities. Sharing personal information in
-those contexts is a great way to foster postive human interaction.  We hope
+those contexts is a great way to foster positive human interaction.  We hope
 that contextual identity will serve as a framework for both developers to

### 2013-02-20 paper.tex
First cut at shrinking paper for w2sp. Remove definitions section and references to it.

@@
 
-\section{Definitions}
-
-Suppose:
-  \begin{itemize}
-    \item $R$ is a set of actors and their relationships to the user. $R$ may include people that the user knows, service providers, or network operators.
-    \item $T$ is a set of tasks and their side-effects. Examples of tasks
-include page navigation, posting to social networks and searching. Examples of
-side-effects include cookies, geolocation data and browser history.
-    \item $p$ is an impression that the user wishes to project, or that actors
-in $R$ perceive. $p$ encompasses such prosaic information as email identifiers
-or session identifiers, or such sentiment as ``Alice is awesome!''
-  \end{itemize}
-
-\begin{definition} We define a contextual identity $I = \{R,T,p\}$, where a user performs tasks
-$T$ in view of or interaction with actors in $R$, while projecting impression
-$p$.
-\end{definition}
-
-A user may have multiple contextual identities $\{I\}$. These identities change
-over time, as users form and dissolve relationships, and focus on different
-sets of tasks. The user's goal is to accomplish tasks in $T$,
-interact with those in $R$ and project $p$ while being able to predict and
-assert control over as much of $I$ as possible.
-
-Our definition focuses on relationships because most privacy concerns stem
-from causing an unexpected exchange of data with people the user
-knows~\cite{wang}. Tasks are key because users are task-oriented, and it is
-easy to map user actions (page navigation, sending email, posting, filling
-forms) to tasks.
-
-\begin{definition}
-A contextual identity violation occurs when the user cannot predict or control
-parameters $R,T,p$.
-\end{definition}
-When a user's tasks are shared with the wrong set $R$, the wrong projected
-identifier $p$ is employed, or a user is perceived as performing tasks $T$ they
-do not anticipate, a violation of the integrity of contextual identity occurs.
-
-\begin{definition}
-Linkage of contextual identities occurs when a set of $\{I\}$ is associated
-with the same user.
-\end{definition}
-
-When this linkage happens against the will or without the knowledge of the
-user, a violation of the integrity of contextual identity occurs.
-
-Using these definitions, we characterize different types of violation by what
-part of the contextual identity the user cannot control, and then show how
-control can be reasserted by a user who employs various mitigation tools.
-
 \section{Contextual identity violations}
@@
 \subsection{Redistributing information out of context}
-(Lack of control over $R$).\\
 Re-distributing information out of its original context often leads to
@@
 
-In all these examples, the audience $R$ of the contextual identity expanded
-without user intervention.
-
 \subsection{Unsatisfiable policies}
 \label{sec:policies}
-(Lack of control over $p$).\\
 Some service providers have policies which preclude isolating multiple
@@
 to participate in these networks without violating the terms of service.  The
-``Real Names'' policy prohibits users from asserting control over $p$.
+``Real Names'' policy prohibits users from asserting control over their identity.
 
 \subsection{User interface errors}
-(Lack of control over $R$).\\
 Even in the absence of changes made by service providers to re-contextualize
@@
 \label{sec:login}
-(Lack of flexibility in $p$).\\
 Facebook Connect is a login platform that allows third-party websites to
@@
 Similar to section~\ref{sec:policies}, many federated login systems simply
-don't have the ability to allow users multiple $p$ values, or identifiers.
+don't have the ability to allow users multiple identifiers.
 Other federated login systems have support for multiple identifiers, but
@@
 do not suffer from this policy or design error~\cite{browserid,oauth},
-giving a user better control over which value of $p$ to employ.
+giving a user better control over which contextual identity to assert.
 
@@
 \label{sec:tracking}
-(Lack of control over $T$, and correlation across values of $p$).\\
 Even if a user does not participate in social networks, they are still subject
@@
 techniques that a dedicated third party could use to collect browsing history
-and link contextual identities through correlation of tasks in $T$ for various
-values of $p$.
+and link contextual identities through correlation of tasks.
 
@@
 \subsection{Automatic mitigations for information leakage}
-Given a set of relationships $R$ and tasks $T$, one can categorize a user's
+Given a set of relationships and tasks, one can categorize a user's
 contextual identities and prevent information leakage between them.  For
@@
 cookies, history, and bookmarks upon entering and exiting this mode are
-different and serve different use cases. Depending on user desire, $R$ when
-using private browsing mode may be other household members, or it may be a
-service to which the user wants to limit cookie leakage.
-%this requires more explanation, omitting for now. A strong contextual
-%identity mechanism allows users control over $R$ or over $T$ when $R$ is
-%clearly identified to them, but the various privacy modes in different web
-%browsers either allows the user control over $T$ or over $R$, but not both at
-%the same time.
+different and serve different use cases. Depending on user desire, the threat
+model for using private browsing mode may be other household members, or it may
+be a service to which the user wants to limit cookie leakage.
 
@@
 Persona is the suite of tools that implements the BrowserID protocol, and it
-supports multiple email identifiers~\cite{browserid}. In this case, when the
-user decides to register for a service using Persona, the task $T$ they are
-performing is authentication, the relationships $R$ are ones they will engage
-in when using the service, and $p$ is tied to the email identifier they use to
-register for the service. Because we can categorize the type of service by URL
+supports multiple email identifiers~\cite{browserid}.
+Because we can categorize the type of service by URL
 as \texttt{about:profile} does, Persona could prompt the user when they're about
 to link the same email identifier to radically different contextual identities,
-such as ones for dating and professional use.  Persona allows the user direct
-control over $p$ given a context {$R,T$} in which they're authenticating.
+such as ones for dating and professional use.
 
@@
 outlived their usefulness, users would benefit from destruction of side-effects
-in $T$ such as cookie data.
+such as cookie data.
 
@@
 last week and redact content that is sensitive or too negative, a frequent cause
-of regret~\cite{wang}.  Redaction allows the user to assert
-better control over $T$ as well as $p$. Although this approach does not help when the service
-provider decides to change the audience on the user's behalf (loss of control
-over $R$), auditing gives the user a good opportunity to review posts that
+of regret~\cite{wang}. 
+ Although this approach does not help when the service
+provider decides to change the audience on the user's behalf, auditing gives the user a good opportunity to review posts that
 might cause regrets. In the case of high-volume users, such a tool could
 incorporate sentiment analysis to aid the user in finding particularly
-problematic content.  This effectively helps users adjust $T$ when $R$ changes
-unexpectedly.
+problematic content.
 
@@
 knows which sites are tracking them, they can choose to block cookies from
-those sites.  This type of tool allows users good control over $R$ by limiting
-who sees the side-effects in $T$.
+those sites.
 
@@
 read-only API}. One way to reduce the likelihood of linked contextual
-identities or assert better control over $p$ would be to provide applications that expire posts after some time.
-Deletion and expiration also reduce $R$ especially in the case of public posts
-and $T$.
-%This would help users better contain the whole context ($R,T$) by segmenting
-%one large audience and one large set of tasks into smaller temporal partitions.
+identities would be to provide applications that expire posts after some time.
+Deletion and expiration also reduce the likely audience especially in the case of public posts
 
@@
 unless they explicitly want to interact with that site~\cite{disconnect}.
-This type of tool (cookie blocker) helps users assert control over audience $R$.
+This type of tool (cookie blocker) helps users assert control over audience.
 
@@
 act against their users' wishes, helping
-users assert control over the effects of their actions $T$.
-
-The Google Sharing project allows users of Google services to confound the way
-Google identifies them~\cite{googlesharing}. In this case $R$ contains Google
-and the Google Sharing proxy. The effect is that users employ a contextual
-identity with a shared $p$. These users employ it only for Google sites not
-requiring login and can accomplish tasks while associating all their actions
-with a random $p$ also associated with many other users.  This devalues $p$ and
-makes it difficult for Google to correlate tasks with a particular user.
-
-Channel encryption systems like TOR\footnote{The Onion Router: \url{https://www.torproject.org}} allow the users more network secrecy; this allows them to better control their audience $R$ by hiding their actions from network operators.
+users assert control over the effects of their actions.
 

### 2013-02-26 paper.tex
switch to ieee
replace authors
minor changes, mostly stubs

@@
-%\documentclass[11pt,letterpaper,onecolumn]{article}
-\documentclass{llncs}
-\usepackage{llncsdoc}
+\documentclass[10pt, conference, compsocconf]{IEEEtran}
 %\usepackage[left=1in,top=1in,right=1in,bottom=1in,nohead]{geometry}
@@
 \usepackage{comment}
-\usepackage{fullpage}
+%\usepackage{fullpage}
 
@@
 
-%\author{Monica Chew,Sid Stamm\\
-%\email{\{mmc,sid\}@mozilla.com}}
+\author{Monica Chew,Sid Stamm\\
+\tt{\{mmc,sid\}@mozilla.com}}
 %\institute{Mozilla}
@@
 
-We provide a simple formalization of the notion of contextual identity, use it
-as a framework to understand existing privacy violations, and analyze
-mitigations for those violations.
+\section{Related Work}
 
-\section{Related Work}
+Barth et al.~provide a formal model for contextual integrity of user
+data~\cite{barth}. The contextual integrity model focuses on the flow of
+personal information in terms of knowledge states held by agents rather than on
+user identity, and works well for modeling privacy legislation and policy. Two
+drawbacks of this work are that it is incapable of modeling information that is
+about more than one person, and it is the type of information rather than the
+content of the information that determines whether or not integrity is
+violated. In the context of social networks, information is rarely ever about a
+single person, and the tone of the message is as important to user
+happiness as the content of the message.
 
@@
 discoverable~\cite{boyd1,chew,nissenbaum}.
-
-Barth et al.~provide a formal model for contextual integrity of user
-data~\cite{barth}. The contextual integrity model focuses on the flow of
-personal information in terms of knowledge states held by agents rather than on
-user identity, and works well for modeling privacy legislation and policy. In
-contrast, this work's model provides a simple framework to understand users'
-ability to represent which contextual identity they want to project, and works
-well for modeling how software features affect users' ability to assert choice
-and control.
 
@@
 
+\section{How do users think about identity?}
+\subsection{Blushproof}
+\subsection{Cookie statistics}
+
 \section{Open problems}
@@
 
+%Convert to IEEE?
 \bibliographystyle{plain}

### 2013-02-28 paper.tex
reorg first page

@@
 
-\title{Contextual Identity: A Framework for Usable Privacy}
+\title{Contextual Identity: Towards Usable Privacy}
 
@@
 \maketitle
+
+\begin{abstract}
+We examine \textit{contextual identity}, a notion that individuals reveal
+different aspects of themselves depending on context. At any given time, they
+may act as a friend, relative, spouse, co-worker, aquaintance, or stranger. We
+analyze contextual identity from the perspective of user choice and control,
+survey contextual identity violations, suggest possible mitigations, and
+propose new resesarch directions to empower users to have better control over their contextual identities.
+\end{abstract}
 \section{Introduction}
@@
 
-People reveal different aspects of themselves depending on context. At any
-given time, they may be acting as a friend, relative, spouse, co-worker,
-acquaintance, or stranger. This observation is not new; Erving Goffman called
-this impression management, and Carl Jung called it persona
-theory~\cite{goffman,jung}. In this short paper, we call it contextual identity.
-%identity as social construct?
-
+The desire for spontaneous, positive human interaction often requires sharing
+personal information. Sharing information can obviously lead to loss of
+privacy, but the act of sharing alone does not negate expectation of privacy~\cite{boyd2}.
 Helen Nissenbaum has long argued that privacy violations come not from the
@@
 information in a way that violates social norms, or in the wrong
-context~\cite{nissenbaum}. The desire for spontaneous, positive human
-interaction often leads to sharing personal information. For example, take
-PatientsLikeMe~\cite{patientslikeme}. This site functions as a support group
-and as a place for people to share health information, such as drug regimens,
-treatment history, side-effects, and more. Though this information is
-traditionally considered extremely sensitive, the users of this site clearly
-value the benefits of sharing: longitudinal graphs of their own health history,
-building community with people who share their disease. Further, sharing
-personal information does not mean that the users don't value
-privacy~\cite{boyd2}. Selling user data originally intended for one purpose for
-another (e.g., to insurance companies to discover uninsurable patients) would
-be a gross violation of users' privacy expectations.
+context~\cite{nissenbaum}.
 
-%this story is a positive story to shock security folk with the breadth and
-%depth of personal information that ordinary users will share
-% instead we could lead with a shocking, negative story like how gay youth get
-% killed when they're outed
+\begin{verbatim}
+NEED NEW EXAMPLE
+gay teen joins facebook group
+megan meier
+amanda todd
+tyler clementi
+http://www.sync-blog.com/sync/2012/10/gay-students-outed-by-facebook-privacy-loophole.html
+http://books.google.ca/books?id=RRUkLhyGZVgC&pg=PA199&lpg=PA199&dq=%22The+days+of+you+having+a+different+image+for+your+work+friends+or+co-workers+and+for+the+other+people+you+know+are+probably+coming+to+an+end+pretty+quickly,%22&source=bl&ots=LRUZf_pd9m&sig=oHHi0qhlHh9prk94gCQFXItjGIg&hl=en&sa=X&ei=ma19UIOhAdOEqQHE2oCADA&ved=0CD8Q6AEwBA#v=onepage&q=%22The%20days%20of%20you%20having%20a%20different%20image%20for%20your%20work%20friends%20or%20co-workers%20and%20for%20the%20other%20people%20you%20know%20are%20probably%20coming%20to%20an%20end%20pretty%20quickly%2C%22&f=false
+\end{verbatim}
 
@@
 searching, indexing, and archiving capabilities, one cannot rely on forgetting
-in online environments~\cite{delete}. Thus, managing contextual identities
+in online environments~\cite{delete}. Managing contextual identities
 online has become increasingly difficult and fraught with mistakes.
-
-One possible solution to this problem is never to post personal information
-online, or at least to consider the entire world might be the audience.
-However, this solution defies human nature. Given that there are 1 billion
-active Facebook users and that 30-40\% of spoken communication is devoted to
-informing others about ourselves, humans are bound to fall short of these
-guidelines~\cite{tamir,fbusers}. The security and privacy community should
-recognize this and develop techniques to meet users' needs rather than
-expecting human nature to change.
 
@@
 
-Barth et al.~provide a formal model for contextual integrity of user
-data~\cite{barth}. The contextual integrity model focuses on the flow of
-personal information in terms of knowledge states held by agents rather than on
-user identity, and works well for modeling privacy legislation and policy. Two
-drawbacks of this work are that it is incapable of modeling information that is
-about more than one person, and it is the type of information rather than the
-content of the information that determines whether or not integrity is
-violated. In the context of social networks, information is rarely ever about a
-single person, and the tone of the message is as important to user
-happiness as the content of the message.
+The notion that individuals inhabit multiple personas has existed in multiple
+fields for many years; Erving Goffman called this impression management, and
+Carl Jung called it persona theory~\cite{goffman,jung}.
+
+Barth, Datta, Mitchell, and Nissenbaum provide a formal model for contextual
+integrity of user data~\cite{barth}. The contextual integrity model focuses on
+the flow of personal information in terms of knowledge states held by agents
+acting in given roles, and works well for modeling privacy legislation such as
+HIPPA and COPPA. Two drawbacks of this work are that it is incapable of
+modeling information where the subject involves more than one person, and it
+only takes the type of information into account rather than the content or tone
+of the information.  Thus, the event ``Bob told Alice that Charlie cooked a
+delicious dinner'' is out of scope of the model.  In the context of social
+networks, information is rarely ever about a single person, and the tone of the
+message is as important to user happiness as the content of the message.
 
@@
 
-\begin{comment}TODO: figure out how to cite this. Why is this short
-paper's model worth pursuing? It's simpler, and focuses on the user rather
-than data.
-\end{comment}
-
 Although network inference and merging attacks are very powerful, at the
 current time they require a level of expertise and resources not available to
-most people. A brief survey of social networking
-advice reveals that the
-major causes of concern come not from a dedicated social graph expert, but people
+most people. A brief survey of social networking advice reveals that the major
+causes of concern come not from a dedicated social graph expert, but people
 close to the user: friends, family, and co-workers~\cite{fbtips2,fbtips1}.
@@
 In December 2007, Google Reader exposed RSS feeds of user-marked news stories
-to the user's Google Talk contacts\footnote{Google Talk contacts are everyone
-with whom a user has chatted, which might include co-workers, supervisors, and
-friends}. Although this feed was always public, prior to this launch it was not
+to the user's Google Talk contacts, which includes everyone
+with whom a user has chatted whether they be co-workers, supervisors, or
+friends. Although this feed was always public, prior to this launch it was not
 discoverable, leading to a bad experience for many users~\cite{helft}. In
@@
 Some service providers have policies which preclude isolating multiple
-contextual identities. For example, Facebook and Google have a ``Real Names'' policy, which
-requires users to register for accounts with their legal
-name~\cite{fb_names,google_names}.  These policies presume the users can be one
-person to everyone. These policies ignore that community-building happens in
-many different contexts, that users have many legitimate reasons for presenting
-different identities in different contexts, and that users don't necessarily
-want those identities to be linked. For example, disallowing avatar handles as
-a primary identifier makes building a gaming community difficult. 
-Linking a gaming identity to a professional identity has already caused
-problems for 2012 Maine Senate candidate and World of Warcraft gamer Colleen
-Lachowicz~\cite{maine}.
+contextual identities. For example, Facebook and Google have a ``Real Names''
+policy, which requires users to register for accounts with their legal
+name~\cite{fb_names,google_names}.  These policies ignore that
+community-building happens in many different contexts, that users have many
+legitimate reasons for presenting different identities in different contexts,
+and that users don't necessarily want those identities to be linked. For
+example, disallowing avatar handles as a primary identifier makes building a
+gaming community difficult.  Linking a gaming identity to a professional
+identity has already caused problems for 2012 Maine Senate candidate and World
+of Warcraft gamer Colleen Lachowicz~\cite{maine}.
 
@@
 to participate in these networks without violating the terms of service.  The
-``Real Names'' policy prohibits users from asserting control over their identity.
+``Real Names'' policy prohibits users from asserting control over their
+identity.
+
+Even worse, many of these providers now serve as login platforms for external
+sites, spreading these unsatisfiable policies outside the service providers
+themselves.  Facebook Connect is a login platform that allows third-party
+websites to authenticate users using their Facebook identity~\cite{fb_connect}.
+Because it is against the terms of service to have multiple Facebook accounts,
+using Facebook Connect has the unwanted side-effect of linking multiple
+contextual identities.
+
+Other federated login systems have support for multiple identifiers, but this
+feature can be poorly implemented or difficult to discover, leading to low use.
+Some login platforms and protocols, such as OAuth and BrowserID, do not suffer
+from this policy or design error~\cite{browserid,oauth}, giving a user better
+control over which contextual identity to assert.
 
@@
 
-\subsection{Federated login}
-\label{sec:login}
-Facebook Connect is a login platform that allows third-party websites to
-authenticate users using their Facebook identity~\cite{fb_connect}. Because it
-is against the terms of service to have multiple Facebook accounts, using
-Facebook Connect has the unwanted side-effect of linking multiple contextual
-identities.
-
-Similar to section~\ref{sec:policies}, many federated login systems simply
-don't have the ability to allow users multiple identifiers.
-Other federated login systems have support for multiple identifiers, but
-this feature can be poorly implemented or difficult to discover, leading to
-low use.
-Some login platforms and protocols, such as OAuth and BrowserID,
-do not suffer from this policy or design error~\cite{browserid,oauth},
-giving a user better control over which contextual identity to assert.
-
 \subsection{Third party tracking}
@@
 expecting users to enumerate their identities and manually curate them is
-probably too burdensome. Firefox has a Profile Manager, but it is so difficult to use that it will be removed.\footnote{See \url{https://bugzilla.mozilla.org/show\_bug.cgi?id=214675\#c53}}.
+probably too burdensome. Firefox has a Profile Manager, but it is so difficult to use that it will be removed.\footnote{See \url{https://bugzilla.mozilla.org/show\_bug.cgi?id=214675\#c53}.}
 
@@
 last week and redact content that is sensitive or too negative, a frequent cause
-of regret~\cite{wang}. 
- Although this approach does not help when the service
-provider decides to change the audience on the user's behalf, auditing gives the user a good opportunity to review posts that
-might cause regrets. In the case of high-volume users, such a tool could
-incorporate sentiment analysis to aid the user in finding particularly
-problematic content.
+of regret~\cite{wang}.  Although this approach does not help when the service
+provider decides to change the audience on the user's behalf, auditing gives
+the user a good opportunity to review posts that might cause regrets. In the
+case of high-volume users, such a tool could incorporate sentiment analysis to
+aid the user in finding particularly problematic content.
 
 Profiles can be generated by user-supplied application-level data, but also
-implicitly through browsing via techniques in Section~\ref{sec:tracking}. Collusion is a
-tool for visualizing cookies~\cite{collusion}, in particular third-party
-cookies set by tracking sites which are typically ad networks.  Once the user
-knows which sites are tracking them, they can choose to block cookies from
-those sites.
+implicitly through browsing via techniques in Section~\ref{sec:tracking}.
+Collusion is a tool for visualizing cookies~\cite{collusion}, in particular
+third-party cookies set by tracking sites which are typically ad networks.
+Once the user knows which sites are tracking them, they can choose to block
+cookies from those sites.
 
 \subsubsection{Remembering to Forget}
-Humans don't have perfect memories, and perhaps social
-networks should not either~\cite{delete}. Many users already engage in manual auditing and
-deletion of old posts~\cite{fbtips2}. A better solution would be to build tools
-that let the user manage this more easily through an API: both Twitter and Facebook provide
-APIs for deletion\footnote{At the time of this writing, Google Plus offers a
-read-only API}. One way to reduce the likelihood of linked contextual
+Humans don't have perfect memories, and perhaps social networks should not
+either~\cite{delete}. Many users already engage in manual auditing and deletion
+of old posts~\cite{fbtips2}. A better solution would be to build tools that let
+the user manage this more easily through an API: both Twitter and Facebook
+provide APIs for deletion\footnote{At the time of this writing, Google Plus
+offers a read-only API.}. One way to reduce the likelihood of linked contextual
 identities would be to provide applications that expire posts after some time.
-Deletion and expiration also reduce the likely audience especially in the case of public posts
-
-\begin{comment}
-\cite{viegas}blogger's expectation of privacy
-\end{comment}
 
@@
 problem~\cite{dnt}. Although Do Not Track is unenforceable from the client
-side, it provides a clear signal to service providers and ad networks
-that the user does not want to be tracked. As adoption increases, ignoring this
-signal will lead to loss of reputation for service providers that explicitly
-act against their users' wishes, helping
-users assert control over the effects of their actions.
+side, it provides a clear signal to service providers and ad networks that the
+user does not want to be tracked. As adoption increases, ignoring this signal
+will lead to loss of reputation for service providers that explicitly act
+against their users' wishes, helping users assert control over the effects of
+their actions.
 
@@
 People have multiple contextual identities. Sharing personal information in
-those contexts is a great way to foster positive human interaction.  We hope
-that contextual identity will serve as a framework for both developers to
-understand their users' privacy needs, and to develop tools that allow users to
-act in their contextual identities in a spontaneous, relaxed, and interesting
-way.
+appropriate contexts fosters positive human interaction.  We hope that
+contextual identity will serve as a useful notion for developers to understand
+their users' privacy needs, and to develop tools that allow users to act in
+their contextual identities in a spontaneous, relaxed, and interesting way.
 

### 2013-02-28 paper.tex
More rewrites for intro

@@
 
-\author{Monica Chew,Sid Stamm\\
-\tt{\{mmc,sid\}@mozilla.com}}
-%\institute{Mozilla}
+\author{\IEEEauthorblockN{Monica Chew, Sid Stamm}
+\IEEEauthorblockA{Mozilla\\
+\tt{\{mmc, sid\}@mozilla.com}}
+}
 \maketitle
@@
 analyze contextual identity from the perspective of user choice and control,
-survey contextual identity violations, suggest possible mitigations, and
-propose new resesarch directions to empower users to have better control over their contextual identities.
+survey contextual identity violations, and propose new resesarch directions to
+empower users to have better control over their contextual identities.
 \end{abstract}
+
 \section{Introduction}
@@
 personal information. Sharing information can obviously lead to loss of
-privacy, but the act of sharing alone does not negate expectation of privacy~\cite{boyd2}.
-Helen Nissenbaum has long argued that privacy violations come not from the
-simple sharing of personal information, but rather from sharing that
-information in a way that violates social norms, or in the wrong
+privacy, but the act of sharing alone does not negate expectation of
+privacy~\cite{boyd2}.  Helen Nissenbaum has long argued that privacy violations
+come not from the simple sharing of personal information, but rather from
+sharing that information in a way that violates social norms, or in the wrong
 context~\cite{nissenbaum}.
 
-\begin{verbatim}
-NEED NEW EXAMPLE
-gay teen joins facebook group
-megan meier
-amanda todd
-tyler clementi
-http://www.sync-blog.com/sync/2012/10/gay-students-outed-by-facebook-privacy-loophole.html
+We consider it a contextual identity violation when
+multiple contextual identities are linked without the user's permission, or the
+user cannot control which contextual identity is presented to a given audience.
+
+Lesbian, gay, bisexual, and transgendered youth are a prime example of this.
+Access to support is crucial for LGTB-identified youth who are at higher risk
+for bullying and suicide than non-LGTB youth, and much of that support is only
+accessible through the Internet in socially conservative areas~\cite{hrc}. In
+2011 Bobbi Duncan and Taylor McCormick, two students at the University of Texas
+at Austin, were inadvertantly outed when their choir director added them to a
+Facebook group for Queer Chorus~\cite{fowler}. Even though both students had
+blocked their parents from seeing any personal posts revealing their sexuality,
+because Queer Chorus is a public group Facebook published notifications to
+Duncan's and McCormick's friends, including their parents. Duncan later
+attempted suicide~\cite{duncan}.
+
+\begin{comment}
+zuckerberg on "having multiple identities is dishonest"
 http://books.google.ca/books?id=RRUkLhyGZVgC&pg=PA199&lpg=PA199&dq=%22The+days+of+you+having+a+different+image+for+your+work+friends+or+co-workers+and+for+the+other+people+you+know+are+probably+coming+to+an+end+pretty+quickly,%22&source=bl&ots=LRUZf_pd9m&sig=oHHi0qhlHh9prk94gCQFXItjGIg&hl=en&sa=X&ei=ma19UIOhAdOEqQHE2oCADA&ved=0CD8Q6AEwBA#v=onepage&q=%22The%20days%20of%20you%20having%20a%20different%20image%20for%20your%20work%20friends%20or%20co-workers%20and%20for%20the%20other%20people%20you%20know%20are%20probably%20coming%20to%20an%20end%20pretty%20quickly%2C%22&f=false
-\end{verbatim}
+\end{comment}
 
@@
 in online environments~\cite{delete}. Managing contextual identities
-online has become increasingly difficult and fraught with mistakes.
+online has become increasingly difficult and fraught with mistakes; we must
+provide users with better tools to control their contextual identities.
 
@@
 
-Although network inference and merging attacks are very powerful, at the
-current time they require a level of expertise and resources not available to
-most people. A brief survey of social networking advice reveals that the major
-causes of concern come not from a dedicated social graph expert, but people
-close to the user: friends, family, and co-workers~\cite{fbtips2,fbtips1}.
-Surveys conducted by Wang et al.~show that typical regrets from posting on
-Facebook stem almost exclusively from fear of negative interactions with people
-that the user knows~\cite{wang}. The consequences of these negative
-interactions can lead to loss of employment or breaking personal relationships.
-Most previous privacy research has focused on distant adversaries, where the
-bad actor is a behavioral tracking service, state agent or unknown
-eavesdropper; in contrast, we assert that users care more about their
-interactions with others close to them.
+Evidence suggests that users' major privacy concerns come from people the user
+knows: friends, family, and co-workers~\cite{fbtips2,fbtips1}.  Surveys
+conducted by Wang et al.~suggest that typical regrets from posting on Facebook
+stem almost exclusively from fear of negative interactions with people that the
+user knows~\cite{wang}. The consequences of these negative interactions can
+lead to loss of employment or breaking personal relationships.  Most previous
+privacy research has focused on distant adversaries, where the bad actor is a
+behavioral tracking service, state agent or unknown eavesdropper; in contrast,
+we assert that users care more about their interactions with others close to
+them.
 
@@
 embarrassment~\cite{nissenbaum}.  In November 2007, Facebook Beacon allowed
-third-party sites to publish purchases, travel bookings, movie rentals and more to the
-user's activity stream.  Because of poor opt-out and lack of visibility into
-what was being published, user outcry was immediate~\cite{mccarthy,nakashima}.
-In December 2007, Google Reader exposed RSS feeds of user-marked news stories
-to the user's Google Talk contacts, which includes everyone
-with whom a user has chatted whether they be co-workers, supervisors, or
-friends. Although this feed was always public, prior to this launch it was not
-discoverable, leading to a bad experience for many users~\cite{helft}. In
-February 2010, Google Buzz launched, a product that
+third-party sites to publish purchases, travel bookings, movie rentals and more
+to the user's activity stream.  Because of poor opt-out and lack of visibility
+into what was being published, user outcry was
+immediate~\cite{mccarthy,nakashima}.  In December 2007, Google Reader exposed
+RSS feeds of user-marked news stories to the user's Google Talk contacts, which
+includes everyone with whom a user has chatted whether they be co-workers,
+supervisors, or friends. Although this feed was always public, prior to this
+launch it was not discoverable, leading to a bad experience for many
+users~\cite{helft}. In February 2010, Google Buzz launched, a product that
 exposed the user's most frequent Gmail and Google Talk contacts and their
@@
 Although wall posts were always visible from profile pages, the new Timeline
-interface brought old wall posts which users used to treat as private
-messages, before the advent of ``Like'' and comment buttons, to the attention
-of an audience that the user never anticipated~\cite{timeline}.
+interface brought old wall posts which users used to treat as private messages,
+before the advent of ``Like'' and comment buttons, to the attention of an
+audience that the user never anticipated~\cite{timeline}.
 
@@
 \subsection{User interface errors}
-Even in the absence of changes made by service providers to re-contextualize
-personal information, it is all too easy for users to broadcast information to
+It is all too easy for users to broadcast information to
 an unintended audience. This phenomenon is so common on Twitter that it has its
@@
 
-\subsection{Third party tracking}
-\label{sec:tracking}
-Even if a user does not participate in social networks, they are still subject
-to tracking by virtue of browsing the web. Third-party cookies, flash cookies,
-web bugs, device fingerprinting, geolocation, history sniffing and more are
-techniques that a dedicated third party could use to collect browsing history
-and link contextual identities through correlation of tasks.
+\section{Research directions}
+We propose new research directions based on the following questions.
+\begin{itemize}
+\item How do users think about identity?
+\item What are users already doing to preserve contextual identities?
+\item What tasks or topics do users find embarrassing?
+\end{itemize}
 
-\section{Possible mitigations}
+plethora of cross posting software, too much damn syndication indicates that
+many users are on multiple platforms.
 
@@
 heuristically or through asking the user, is paramount to helping the user
-manage it.
-Although a user may subconsciously be aware of their contextual identities,
-expecting users to enumerate their identities and manually curate them is
-probably too burdensome. Firefox has a Profile Manager, but it is so difficult to use that it will be removed.\footnote{See \url{https://bugzilla.mozilla.org/show\_bug.cgi?id=214675\#c53}.}
+manage it.  Although a user may subconsciously be aware of their contextual
+identities, expecting users to enumerate their identities and manually curate
+them is probably too burdensome. Firefox has a Profile Manager, but it is so
+difficult to use that it will be removed.\footnote{See
+\url{https://bugzilla.mozilla.org/show\_bug.cgi?id=214675\#c53}.}
 
@@
 \subsection{Automatic mitigations for information leakage}
-Given a set of relationships and tasks, one can categorize a user's
-contextual identities and prevent information leakage between them.  For
-example, preventing third-party cookies from being read and set across task
-boundaries means that targeted ads for dating would not follow the user when
-visiting a technology news site. Knowing the user's current contextual identity
-also allows the browser to suppress URL bar suggestions that aren't relevant to
-that identity, protecting the user from both shoulder-surfing and distraction.
+One can categorize a user's contextual identities and prevent information
+leakage between them.  For example, preventing third-party cookies from being
+read and set across task boundaries means that targeted ads for dating would
+not follow the user when visiting a technology news site. Knowing the user's
+current contextual identity also allows the browser to suppress URL bar
+suggestions that aren't relevant to that identity, protecting the user from
+both shoulder-surfing and distraction.
 
@@
 Profiles can be generated by user-supplied application-level data, but also
-implicitly through browsing via techniques in Section~\ref{sec:tracking}.
+implicitly through browsing via tracking techniques.
 Collusion is a tool for visualizing cookies~\cite{collusion}, in particular
@@
 
-\section{How do users think about identity?}
-\subsection{Blushproof}
-\subsection{Cookie statistics}
-
-\section{Open problems}
-We are largely ignorant of the ways in which users think about contextual
-identity. Building usable software to manage contextual identity demands
-further research.
-
-The mitigations proposed in this work become more complex in the face of shared
-devices and overlapping identities. There are good reasons to want to intermix
-work and personal identities (increased exposure, serendipitous connections)
-and so many people use the same account for both personal and work reasons.
-
-Mobile growth is driving most internet growth, and much of that growth comes
-developing countries. The literature on how device sharing works in those
-markets is completely lacking. Managing contextual identities on shared devices
-promises to be a difficult problem.
-
-\section{Discussion}
+\section{Summary}
 People have multiple contextual identities. Sharing personal information in
@@
 their contextual identities in a spontaneous, relaxed, and interesting way.
-
-\begin{comment}
-papers:
-expectation of privacy\cite{viegas}
-http://jcmc.indiana.edu/vol10/issue3/viegas.html
-
-danah boyd
-making sense of privacy and publicity: whose voice counts? does your child's
-teacher have a right to be public in her other roles online? does she have a
-right to be secular? religious? friend? lover? if you work for company X and
-you disagree with their policies, are you allowed to be public about
-that:?\cite{boyd2}
-
-close to you “stranger on a train” “stranger on a plane”
-first party regrets, third party regrets
-impossible to judge how big friends of friends
-
-\end{comment}
 

### 2013-02-28 paper.tex
more rewrites

@@
 
-The desire for spontaneous, positive human interaction often requires sharing
-personal information. Sharing information can obviously lead to loss of
-privacy, but the act of sharing alone does not negate expectation of
-privacy~\cite{boyd2}.  Helen Nissenbaum has long argued that privacy violations
-come not from the simple sharing of personal information, but rather from
-sharing that information in a way that violates social norms, or in the wrong
-context~\cite{nissenbaum}.
+The desire for privacy balances the desire for spontaneous, positive human
+interaction, which often requires sharing personal information.  The act of
+sharing alone does not negate expectation of privacy~\cite{boyd2}. Helen
+Nissenbaum has long argued that privacy violations come not from the simple
+sharing of personal information, but rather from sharing that information in a
+way that violates social norms, or in the wrong context~\cite{nissenbaum}.
 
-We consider it a contextual identity violation when
-multiple contextual identities are linked without the user's permission, or the
-user cannot control which contextual identity is presented to a given audience.
-
-Lesbian, gay, bisexual, and transgendered youth are a prime example of this.
-Access to support is crucial for LGTB-identified youth who are at higher risk
-for bullying and suicide than non-LGTB youth, and much of that support is only
-accessible through the Internet in socially conservative areas~\cite{hrc}. In
-2011 Bobbi Duncan and Taylor McCormick, two students at the University of Texas
-at Austin, were inadvertantly outed when their choir director added them to a
-Facebook group for Queer Chorus~\cite{fowler}. Even though both students had
-blocked their parents from seeing any personal posts revealing their sexuality,
-because Queer Chorus is a public group Facebook published notifications to
-Duncan's and McCormick's friends, including their parents. Duncan later
-attempted suicide~\cite{duncan}.
+Lesbian, gay, bisexual, and transgendered youth are at risk for contextual
+identity violations.  Access to support is crucial for LGTB-identified youth
+who are at higher risk for bullying and suicide than non-LGTB youth, and much
+of that support is only accessible through the Internet in socially
+conservative areas~\cite{hrc}. In 2011 Bobbi Duncan and Taylor McCormick, two
+students at the University of Texas at Austin, were inadvertantly outed when
+their choir director added them to a Facebook group for Queer
+Chorus~\cite{fowler}. Even though both students had blocked their parents from
+seeing any personal posts revealing their sexuality, because Queer Chorus is a
+public group Facebook published notifications to Duncan's and McCormick's
+friends, including their parents. Duncan later attempted suicide~\cite{duncan}.
 
@@
 acting in given roles, and works well for modeling privacy legislation such as
-HIPPA and COPPA. Two drawbacks of this work are that it is incapable of
-modeling information where the subject involves more than one person, and it
+HIPPA and COPPA. Two drawbacks of this work are that it does not
+model information where the subject involves more than one person, and it
 only takes the type of information into account rather than the content or tone
-of the information.  Thus, the event ``Bob told Alice that Charlie cooked a
+of the information.  ``Bob told Alice that Charlie cooked a
 delicious dinner'' is out of scope of the model.  In the context of social
-networks, information is rarely ever about a single person, and the tone of the
-message is as important to user happiness as the content of the message.
+networks, information is rarely about a single person, and the tone of the
+message is as important to user effect as the content of the message.
 
@@
 \section{Contextual identity violations}
+We consider it a contextual identity violation when
+multiple contextual identities are linked without the user's permission, or the
+user cannot control which contextual identity is presented to a given audience.
+
 \label{sec:examples}
@@
 
-\subsection{Unsatisfiable policies}
+\subsection{Policy errors}
 \label{sec:policies}
@@
 \item How do users think about identity?
+\item What can we infer about identity?
+\item What threat models (audiences, topics) are important to users?
 \item What are users already doing to preserve contextual identities?
-\item What tasks or topics do users find embarrassing?
 \end{itemize}
 
-plethora of cross posting software, too much damn syndication indicates that
-many users are on multiple platforms.
+\subsection{How do users think about identity?}
+Users' contextual identities may be task-oriented, service-oriented,
+relationship-oriented, or guided by other principles. The long-time existence
+of support for multiple accounts in email clients suggests that many users have
+multiple email identifiers, which could be considered as a proxy for identity
+if tied to service accounts. Similarly, data suggests that a large minority of
+Twitter users have multiple Twitter accounts, and the plethora of cross-posting
+or syndication software from one social network to another suggests that many
+users take advantage of multiple social networks~\cite{twitter,xpost}.  That is
+not to say that all users have the same tolerance or even need for multiple
+explicit identities: in fact many users may be exclusively task-oriented and
+use the Internet with specific tasks in mind rather than for social interaction
+or exploratory surfing\footnote{Even these users are subject to building
+implicit identities through the use of tracking techniques, however.}.
 
-\subsection{Inferring contextual identities}
-Accurately detecting the user's current contextual identity, whether
-heuristically or through asking the user, is paramount to helping the user
-manage it.  Although a user may subconsciously be aware of their contextual
-identities, expecting users to enumerate their identities and manually curate
-them is probably too burdensome. Firefox has a Profile Manager, but it is so
-difficult to use that it will be removed.\footnote{See
-\url{https://bugzilla.mozilla.org/show\_bug.cgi?id=214675\#c53}.}
-
-Tang et al.~show that most people do not take the time to create labels and
-maintain friend lists~\cite{tang}. However, the same authors show how to use
+Although a user may subconsciously be aware of their contextual identities,
+expecting users to enumerate their identities and manually curate them is
+probably too burdensome. Firefox has a Profile Manager, but it is so difficult
+to use that it will be removed.\footnote{See
+\url{https://bugzilla.mozilla.org/show\_bug.cgi?id=214675\#c53}.} Tang et
+al.~show that most people do not take the time to create labels and maintain
+friend lists~\cite{tang}. However, the same authors show how to use
 heterogeneous networks to infer relationship types (e.g., manager-subordinate)
@@
 
-It may also be possible to infer tasks from the user's activity. For example,
-the \texttt{about:profile} Firefox extension uses the Open Directory Project
-and Alexa to categorize URLs that the user has visited~\cite{aboutprofile}.
+Further research is required to determine what constitutes a contextual
+identity. The contextual integrity model from Barth et al.~does not capture
+these notions adequately.
+
+(This is weak)
+If users' contextual identities are primarily task oriented, it may be
+possible to infer tasks from the user's activity. For example, the
+\texttt{about:profile} Firefox extension uses the Open Directory Project and
+Alexa to categorize URLs that the user has visited~\cite{aboutprofile}.
 

### 2013-02-28 paper.tex
trivial tweaks, nothing substantial

@@
 also true that in offline environments, humans don't have perfect memories and
-will eventually forget.  However, with the advent of increasingly vast
+will often eventually forget.  However, with the advent of increasingly vast
 searching, indexing, and archiving capabilities, one cannot rely on forgetting
@@
 acting in given roles, and works well for modeling privacy legislation such as
-HIPPA and COPPA. Two drawbacks of this work are that it does not
+HIPPA and COPPA. Two limitations of this work are that it does not
 model information where the subject involves more than one person, and it
@@
 We consider it a contextual identity violation when
-multiple contextual identities are linked without the user's permission, or the
-user cannot control which contextual identity is presented to a given audience.
+multiple contextually-separate identities are linked without the user's
+permission, or when the user cannot select which contextual identity is
+presented to a given audience.
 

### 2013-02-28 paper.tex
label, label

@@
 \item How do users think about identity?
-\item What can we infer about identity?
-\item What threat models (audiences, topics) are important to users?
-\item What are users already doing to preserve contextual identities?
+\item How do users manage identity?
+\item How can we improve tools for managing identity?
 \end{itemize}
@@
 
+\subsection{How do users manage identity?}
+\paragraph{Profile management}
 Although a user may subconsciously be aware of their contextual identities,
@@
 
-Further research is required to determine what constitutes a contextual
-identity. The contextual integrity model from Barth et al.~does not capture
-these notions adequately.
-
-(This is weak)
-If users' contextual identities are primarily task oriented, it may be
-possible to infer tasks from the user's activity. For example, the
-\texttt{about:profile} Firefox extension uses the Open Directory Project and
-Alexa to categorize URLs that the user has visited~\cite{aboutprofile}.
-
-\subsection{Automatic mitigations for information leakage}
-One can categorize a user's contextual identities and prevent information
-leakage between them.  For example, preventing third-party cookies from being
-read and set across task boundaries means that targeted ads for dating would
-not follow the user when visiting a technology news site. Knowing the user's
-current contextual identity also allows the browser to suppress URL bar
-suggestions that aren't relevant to that identity, protecting the user from
-both shoulder-surfing and distraction.
-
+\paragraph{Private browsing mode}
 Privacy modes in Firefox, Chrome, Safari, and Opera are a good first step, but
@@
 
+\subsection{How can we improve identity management tools?}
+If users' contextual identities are primarily task-oriented, it may be
+possible to infer tasks from the user's activity. For example, the
+\texttt{about:profile} Firefox extension uses the Open Directory Project and
+Alexa to categorize URLs that the user has visited~\cite{aboutprofile}.
+
+\paragraph{Mitigating information leaks}
+Given a user's contextual identities, we may be able to prevent information
+leakage between them.  For example, preventing third-party cookies from being
+read and set across task boundaries means that targeted ads for dating would
+not follow the user when visiting a technology news site. Knowing the user's
+current contextual identity also allows the browser to suppress URL bar
+suggestions that aren't relevant to that identity, protecting the user from
+both shoulder-surfing and distraction.
+
+\paragraph{Mitigating unwanted linkage}
 Another partial solution is to prompt the user when they're about to link

### 2013-03-01 paper.tex
more reorg

@@
 who your intended audience is, how many people will overhear you, and how
-likely your information is to be re-broadcast in a different context. It is
-also true that in offline environments, humans don't have perfect memories and
-will often eventually forget.  However, with the advent of increasingly vast
+likely your information is to be re-broadcast in a different context. 
+In offline environments, humans don't have perfect memories and
+will typically forget.  However, with the advent of increasingly vast
 searching, indexing, and archiving capabilities, one cannot rely on forgetting
@@
 \section{Contextual identity violations}
-We consider it a contextual identity violation when
-multiple contextually-separate identities are linked without the user's
-permission, or when the user cannot select which contextual identity is
-presented to a given audience.
+We consider it a contextual identity violation when multiple identities are
+linked without user intent, or when the user cannot choose which contextual
+identity to assert.
 
@@
 \subsection{How do users think about identity?}
+It is unlikely that the majority of users are consciously aware of having
+multiple contextual identities. Imagine two users at the opposite ends of the
+spectrum:
+\begin{itemize}
+\item A user who participates in no social networks, reads paper newspapers,
+uses the Internet for well-defined tasks (e.g., coordinating visits with
+friends over email, looking up restaurant reviews) but does not otherwise
+engage in discretionary browsing.
+\item A savvy user who is active on Facebook, Twitter, Instagram and has
+different posting levels, topics, and followers on each, maintains multiple
+email accounts and pseudonyms, is online multiple hours daily for both work and
+personal reasons. 
+\end{itemize}
+
+The second user may be much more aware of contextual identities, but even the
+first user would benefit from protection against contextual identity
+violations. For example, engaging in a long-term task such as house-buying
+often requires the construction of a contextual identity. The tasks associated
+with this identity have an externally imposed end date and may have long-lived
+side-effects, such as long-term cookies that reveal sensitive information
+(e.g., the neighborhood of the house purchase, income information derived from
+purchases, other demographic data). For contextual identities that have
+outlived their usefulness, users would benefit from destruction of side-effects
+such as cookie data.
+
 Users' contextual identities may be task-oriented, service-oriented,
@@
 \subsection{How do users manage identity?}
+\paragraph{Private browsing mode}
+Privacy modes in Firefox, Chrome, Safari, and Opera are a good first step, but
+are no means a complete solution~\cite{ABBJ10}. There is no standard behavior
+for private browsing mode, and thus interaction with extensions, treatment of
+cookies, history, and bookmarks upon entering and exiting this mode are
+different and serve different use cases. Depending on user desire, the threat
+model for using private browsing mode may be other household members, or it may
+be a service to which the user wants to limit cookie leakage.
+
 \paragraph{Profile management}
@@
 
-\paragraph{Private browsing mode}
-Privacy modes in Firefox, Chrome, Safari, and Opera are a good first step, but
-are no means a complete solution~\cite{ABBJ10}. There is no standard behavior
-for private browsing mode, and thus interaction with extensions, treatment of
-cookies, history, and bookmarks upon entering and exiting this mode are
-different and serve different use cases. Depending on user desire, the threat
-model for using private browsing mode may be other household members, or it may
-be a service to which the user wants to limit cookie leakage.
-
 \subsection{How can we improve identity management tools?}
@@
 
-\paragraph{Mitigating information leaks}
+\paragraph{Mitigating implicit linkage}
 Given a user's contextual identities, we may be able to prevent information
@@
 
-\paragraph{Mitigating unwanted linkage}
+\paragraph{Mitigating explicit unwanted linkage}
 Another partial solution is to prompt the user when they're about to link
@@
 
-\subsection{Expiring contextual identities}
-Oftentimes a user may have a long-term task, such as wedding planning or house
-buying, that requires constructing a contextual identity. The tasks associated
-with this identity have an externally imposed end date and may have long-lived
-side-effects, such as long-term cookies that reveal sensitive information
-(e.g., the neighborhood of the house purchase, income information derived from
-purchases, other demographic data). For contextual identities that have
-outlived their usefulness, users would benefit from destruction of side-effects
-such as cookie data.
+\paragraph{Controlling Information Flow}
+Sometimes a user might want to prevent mistakes from being made in the first
+place. If a user is concerned about a particular service provider, they can
+install an extension like Disconnect to disallow cookies from that provider
+unless they explicitly want to interact with that site~\cite{disconnect}.
+This type of tool (cookie blocker) helps users assert control over audience.
 
-\subsection{Recovering from Mistakes}
-\subsubsection{Auditing}
+Protocols like Do Not Track are also a good first step to solving this
+problem~\cite{dnt}. Although Do Not Track is unenforceable from the client
+side, it provides a clear signal to service providers and ad networks that the
+user does not want to be tracked. As adoption increases, ignoring this signal
+will lead to loss of reputation for service providers that explicitly act
+against their users' wishes, helping users assert control over the effects of
+their actions.
+
+\paragraph{Auditing}
 A major cause of user embarrassment is exposing information to the wrong
@@
 
-\subsubsection{Remembering to Forget}
+\paragraph{Remembering to Forget}
 Humans don't have perfect memories, and perhaps social networks should not
@@
 the user manage this more easily through an API: both Twitter and Facebook
-provide APIs for deletion\footnote{At the time of this writing, Google Plus
+provide APIs for post deletion\footnote{Google Plus
 offers a read-only API.}. One way to reduce the likelihood of linked contextual
@@
 
-\subsection{Preventing Mistakes}
-\subsubsection{Controlling Information Flow}
-Sometimes a user might want to prevent mistakes from being made in the first
-place. If a user is concerned about a particular service provider, they can
-install an extension like Disconnect to disallow cookies from that provider
-unless they explicitly want to interact with that site~\cite{disconnect}.
-This type of tool (cookie blocker) helps users assert control over audience.
-
-Protocols like Do Not Track are also a good first step to solving this
-problem~\cite{dnt}. Although Do Not Track is unenforceable from the client
-side, it provides a clear signal to service providers and ad networks that the
-user does not want to be tracked. As adoption increases, ignoring this signal
-will lead to loss of reputation for service providers that explicitly act
-against their users' wishes, helping users assert control over the effects of
-their actions.
-
-\subsubsection{Visual reminders of context}
+\paragraph{Visual reminders of context}
 To mitigate privacy violations caused by poor user interfaces, the onus must be

### 2013-03-02 paper.tex
mostly rewritten

@@
 only takes the type of information into account rather than the content or tone
-of the information.  ``Bob told Alice that Charlie cooked a
+of the information. For example, ``Bob told Alice that Charlie cooked a
 delicious dinner'' is out of scope of the model.  In the context of social
 networks, information is rarely about a single person, and the tone of the
-message is as important to user effect as the content of the message.
+message is as important to user effect as the contents.
 
-Many authors have discovered attacks to link different contextual identities to
+Many authors have discovered methods to link different contextual identities to
 the same person. Narayanan and Shmatikov present a re-identification technique
@@
 linked~\cite{narayanan1,narayanan2}. Lindamood et al.~and Mislove et al.~show
-how to infer previously undisclosed information from released social networking
+how to infer previously undisclosed information from public social networking
 data~\cite{lindamood,mislove}.
@@
 \section{Contextual identity violations}
-We consider it a contextual identity violation when multiple identities are
-linked without user intent, or when the user cannot choose which contextual
-identity to assert.
+In this section we discuss three types of \textit{contextual identity
+violations}. We consider a contextual identity violation to be when multiple
+identities are linked without user intent, or when the user cannot choose which
+contextual identity to assert in a given situation. In these examples the user
+may not be conscious of what a contextual identity is: nevertheless each
+example illustrates a loss of user control over what aspects of self to
+reveal in a given context.
 
@@
 message instead of a private, direct message. Representative Anthony Weiner was
-a victim of this mistake when he inadvertently sent compromising pictures of
-himself publicly~\cite{weiner}. Considering that this mistake requires
+a victim of this mistake when he inadvertently published compromising pictures
+of himself~\cite{weiner}. Considering that this mistake requires
 mistyping a single character (\texttt{@} instead of \texttt{d}), it's no
@@
 \subsection{How do users think about identity?}
-It is unlikely that the majority of users are consciously aware of having
-multiple contextual identities. Imagine two users at the opposite ends of the
-spectrum:
+We hypothesize many users are not consciously aware of having multiple
+contextual identities. In order to develop tools to help users, we need to
+understand users' mental models of identity and how information is shared on
+the Internet. For computer scientists, authentication is tied to identity, and
+even in the absence of authentication, using the same device over time
+implicitly creates an identity through tracking techniques and local
+information. However, these points are far from obvious to a typical user,
+especially for users who don't distinguish the web application from the
+browser, from the operating system, or from the device.
+
+The computer science community must free itself from software-specific
+notions of identity if we are to help users to whom the very concept of
+identity is an enigma. To start understanding our users' mental models,
+one might start with the questions:
+
 \begin{itemize}
-\item A user who participates in no social networks, reads paper newspapers,
-uses the Internet for well-defined tasks (e.g., coordinating visits with
-friends over email, looking up restaurant reviews) but does not otherwise
-engage in discretionary browsing.
-\item A savvy user who is active on Facebook, Twitter, Instagram and has
-different posting levels, topics, and followers on each, maintains multiple
-email accounts and pseudonyms, is online multiple hours daily for both work and
-personal reasons. 
+\item How is identity represented online?
+\item Is your identity tied to the device you are using?
+\item If you check your mail, read news, log on to a social network at a
+computer at the public library, does that affect your identity?
+\item What does it mean to share devices? If you lend your tablet to your
+sister, is she representing herself, or you?
+\item If you register for an account on a service, do you expect that to have
+an influence on your online identity? What if you never use that account again?
+\item If you visit a website, do you expect that to have an influence on your
+browsing experience or online identity? If so, for how long?
+\item Which parts of your online identity do you expect to be visible to
+your housemates, friends, relatives, or employers?
+\item Which parts of your identity do you want to share with whom?
+\item Which parts of your identity do you want to keep secret from whom?
+\item How does your identity change over time?
 \end{itemize}
 
-The second user may be much more aware of contextual identities, but even the
-first user would benefit from protection against contextual identity
-violations. For example, engaging in a long-term task such as house-buying
-often requires the construction of a contextual identity. The tasks associated
-with this identity have an externally imposed end date and may have long-lived
-side-effects, such as long-term cookies that reveal sensitive information
-(e.g., the neighborhood of the house purchase, income information derived from
-purchases, other demographic data). For contextual identities that have
-outlived their usefulness, users would benefit from destruction of side-effects
-such as cookie data.
-
-Users' contextual identities may be task-oriented, service-oriented,
-relationship-oriented, or guided by other principles. The long-time existence
-of support for multiple accounts in email clients suggests that many users have
-multiple email identifiers, which could be considered as a proxy for identity
-if tied to service accounts. Similarly, data suggests that a large minority of
-Twitter users have multiple Twitter accounts, and the plethora of cross-posting
-or syndication software from one social network to another suggests that many
-users take advantage of multiple social networks~\cite{twitter,xpost}.  That is
-not to say that all users have the same tolerance or even need for multiple
-explicit identities: in fact many users may be exclusively task-oriented and
-use the Internet with specific tasks in mind rather than for social interaction
-or exploratory surfing\footnote{Even these users are subject to building
-implicit identities through the use of tracking techniques, however.}.
+danah boyd has done excellent work surveying youth and social networks, and Pew
+Internet is a good source for self-reported phone surveys on privacy and social
+media, but there is otherwise a dearth of research in these
+areas~\cite{boyd,pew1,pew2,pew3}.
 
 \subsection{How do users manage identity?}
+
+Users who are aware of having multiple identities engage in the following
+identity management techniques.
+
+\paragraph{Multiple accounts}
+The long-time existence of support for multiple accounts in email clients
+suggests that many users have multiple email identifiers, which could be
+considered as a proxy for identity if tied to service accounts. Similarly, data
+suggests that a large minority of Twitter users have multiple Twitter accounts,
+and the plethora of cross-posting or syndication software from one social
+network to another suggests that many users take advantage of multiple social
+networks~\cite{twitter}.
+\begin{comment}
+That is not to say that all users have the same
+tolerance or even need for multiple explicit identities: in fact many users may
+be exclusively task-oriented and use the Internet with specific tasks in mind
+rather than for social interaction or exploratory surfing\footnote{Even these
+users are subject to building implicit identities through the use of tracking
+techniques, however.}.
+\end{comment}
+
+\paragraph{Auditing}
+Wang et.~al suggest that common techniques for handling regret online include
+manual deletion of regrettable posts, self-censoring or delaying
+posts that they predict might bring regret~\cite{wang}.
+
 \paragraph{Private browsing mode}
-Privacy modes in Firefox, Chrome, Safari, and Opera are a good first step, but
-are no means a complete solution~\cite{ABBJ10}. There is no standard behavior
-for private browsing mode, and thus interaction with extensions, treatment of
-cookies, history, and bookmarks upon entering and exiting this mode are
-different and serve different use cases. Depending on user desire, the threat
-model for using private browsing mode may be other household members, or it may
-be a service to which the user wants to limit cookie leakage.
+Private browsing mode exists in all major browsers, but are not a complete
+solution~\cite{ABBJ10}. There is no standard behavior for private browsing
+mode, and interaction with extensions, treatment of cookies, history, and
+bookmarks upon entering and exiting this mode are different and serve different
+use cases. For example, entering private browsing in Firefox does not clear
+cookies, history, or other session data; session data is cleared on exiting
+private browsing mode. In contrast, incognito mode in Chrome makes previous
+session state unavailable and clears new session state on exit; this mode
+may be preferable as a ``Guest mode'' where the device owner does not want the
+guest to either view or pollute existing state.
 
@@
 expecting users to enumerate their identities and manually curate them is
-probably too burdensome. Firefox has a Profile Manager, but it is so difficult
-to use that it will be removed.\footnote{See
-\url{https://bugzilla.mozilla.org/show\_bug.cgi?id=214675\#c53}.} Tang et
-al.~show that most people do not take the time to create labels and maintain
-friend lists~\cite{tang}. However, the same authors show how to use
-heterogeneous networks to infer relationship types (e.g., manager-subordinate)
-though the graph itself is unlabeled.
+probably too burdensome. Firefox has a Profile Manager, but it is so unusable
+that it will be removed.\footnote{See
+\url{https://bugzilla.mozilla.org/show\_bug.cgi?id=214675\#c53}.}
+
+\paragraph{Cookie blockers}
+Disconnect and ShareMeNot are browser extensions to disallow interacting with
+service providers like Google and Facebook unless users explicitly choose to
+interact with that site~\cite{disconnect,franzi}.
 
 \subsection{How can we improve identity management tools?}
+\paragraph{Task inference}
 If users' contextual identities are primarily task-oriented, it may be
@@
 Alexa to categorize URLs that the user has visited~\cite{aboutprofile}.
+
+\paragraph{Relationship inference}
+Tang et al.~show that most people do not take the time to create labels and
+maintain friend lists~\cite{tang}. However, the same authors show how to use
+heterogeneous networks to infer relationship types (e.g., manager-subordinate)
+though the graph itself is unlabeled.
 
@@
 
-\paragraph{Mitigating explicit unwanted linkage}
+\paragraph{Mitigating explicit linkage}
 Another partial solution is to prompt the user when they're about to link
@@
 \paragraph{Controlling Information Flow}
-Sometimes a user might want to prevent mistakes from being made in the first
-place. If a user is concerned about a particular service provider, they can
-install an extension like Disconnect to disallow cookies from that provider
-unless they explicitly want to interact with that site~\cite{disconnect}.
-This type of tool (cookie blocker) helps users assert control over audience.
-
-Protocols like Do Not Track are also a good first step to solving this
-problem~\cite{dnt}. Although Do Not Track is unenforceable from the client
-side, it provides a clear signal to service providers and ad networks that the
-user does not want to be tracked. As adoption increases, ignoring this signal
-will lead to loss of reputation for service providers that explicitly act
-against their users' wishes, helping users assert control over the effects of
-their actions.
+Do Not Track is an HTTP request header that signals to the website that the
+user does not want to be tracked~\cite{dnt}. Although Do Not Track is
+unenforceable from the client side, service providers who ignore signal will
+lose reputation by acting against their users' explicit wishes.
 
@@
 A major cause of user embarrassment is exposing information to the wrong
-audience, as illustrated in section~\ref{sec:examples}. A browser is in an
-ideal position to intermediate social network posts, aggregate them locally,
-and present them to the user when they desire to audit their digital footprint.
-For example, a user could see all of the comments and posts they made in the
-last week and redact content that is sensitive or too negative, a frequent cause
-of regret~\cite{wang}.  Although this approach does not help when the service
-provider decides to change the audience on the user's behalf, auditing gives
-the user a good opportunity to review posts that might cause regrets. In the
-case of high-volume users, such a tool could incorporate sentiment analysis to
-aid the user in finding particularly problematic content.
+audience. A browser is in an ideal position to intermediate social network
+posts, aggregate them locally, and present them to the user when they desire to
+audit their digital footprint.  For example, a user could see all of the
+comments and posts they made in the last week and redact content that is
+sensitive or too negative, a frequent cause of regret~\cite{wang}.  Although
+this approach does not help when the service provider decides to change the
+audience on the user's behalf, auditing gives the user a good opportunity to
+review posts that might cause regrets. In the case of high-volume users, such a
+tool could incorporate sentiment analysis to aid the user in finding
+particularly problematic content.
 
+\paragraph{Implicit identity generation}
 Profiles can be generated by user-supplied application-level data, but also
-implicitly through browsing via tracking techniques.
-Collusion is a tool for visualizing cookies~\cite{collusion}, in particular
-third-party cookies set by tracking sites which are typically ad networks.
-Once the user knows which sites are tracking them, they can choose to block
-cookies from those sites.
+implicitly through browsing via tracking techniques.  Collusion is a tool for
+visualizing cookies~\cite{collusion}, in particular third-party cookies set by
+tracking sites which are typically ad networks.  Once the user knows which
+sites are tracking them, they can choose to block cookies from those sites.
 
-\paragraph{Remembering to Forget}
+\paragraph{Visual reminders of context}
+To mitigate privacy violations caused by poor user interfaces, the software
+must provide sufficient visual cues of context. For example, many but not all
+Google products support multiple accounts. However, the visual cue to indicate
+which account is active is a small, easy to ignore text name at the top right
+of the page.
+
+\paragraph{Expiring posts}
 Humans don't have perfect memories, and perhaps social networks should not
@@
 
-\paragraph{Visual reminders of context}
-To mitigate privacy violations caused by poor user interfaces, the onus must be
-on software developers to provide sufficient visual cues of context. For
-example, many but not all Google products support multiple accounts. However,
-the visual cue to indicate which account is active is a small, easy to ignore
-text name at the top right of the page.
-
-Much work has been done for visual verification of domain authenticity in the
-context of phishing, but not much has been done for visual verification of
-which user credentials are active~\cite{skins}.
+\paragraph{Expiring contextual identities}
+Engaging in a long-term task such as house-buying
+often requires the construction of a contextual identity. The tasks associated
+with this identity have an externally imposed end date and may have long-lived
+side-effects, such as long-term cookies that reveal sensitive information
+(e.g., the neighborhood of the house purchase, income information derived from
+purchases, other demographic data). For contextual identities that have
+outlived their usefulness, users would benefit from destruction of side-effects
+such as cookie data.
 
@@
 Mike Connor
-Ed Lee
+Chris Karlof
 \end{comment}
 
-%Convert to IEEE?
 \bibliographystyle{plain}

### 2013-03-03 paper.tex
still rewriting last section

@@
 interaction, which often requires sharing personal information. The act of
-sharing alone does not negate expectation of privacy~\cite{boyd2}. Helen
-Nissenbaum has long argued that privacy violations come not from the simple
-sharing of personal information, but rather from sharing that information in a
-way that violates social norms, or in the wrong context~\cite{nissenbaum}.
+sharing alone does not negate expectation of privacy~\cite{boyd2}.
+%The desire for spontaneous, positive human interaction often requires sharing
+%personal information. Sharing information can lead to loss of privacy, though
+%it does not negate expectation of privacy~\cite{boyd2}. 
+Helen Nissenbaum has long argued that privacy violations come not from the
+simple sharing of personal information, but rather from sharing that
+information in a way that violates social norms, or in the wrong
+context~\cite{nissenbaum}.
 
 Lesbian, gay, bisexual, and transgendered youth are at risk for contextual
-identity violations.  Access to support is crucial for LGTB-identified youth
-who are at higher risk for bullying and suicide than non-LGTB youth, and much
-of that support is only accessible through the Internet in socially
-conservative areas~\cite{hrc}. In 2011 Bobbi Duncan and Taylor McCormick, two
+identity violations.  Access to support is crucial for LGTB-identified youth,
+who are at higher risk for bullying and suicide than non-LGTB youth~\cite{hrc}.
+Much of that support is only accessible through the Internet in socially
+conservative areas. In 2011 Bobbi Duncan and Taylor McCormick, two
 students at the University of Texas at Austin, were inadvertantly outed when
@@
 Many authors have discovered methods to link different contextual identities to
-the same person. Narayanan and Shmatikov present a re-identification technique
+an individual. Narayanan and Shmatikov present a re-identification technique
 to merge anonymized social graphs from different networks and prove that
@@
 Although wall posts were always visible from profile pages, the new Timeline
-interface brought old wall posts which users used to treat as private messages,
+interface brought old wall posts, which users used to treat as private messages
 before the advent of ``Like'' and comment buttons, to the attention of an
@@
 Even worse, many of these providers now serve as login platforms for external
-sites, spreading these unsatisfiable policies outside the service providers
-themselves.  Facebook Connect is a login platform that allows third-party
-websites to authenticate users using their Facebook identity~\cite{fb_connect}.
-Because it is against the terms of service to have multiple Facebook accounts,
-using Facebook Connect has the unwanted side-effect of linking multiple
-contextual identities.
+sites. For example, Facebook Connect allows third-party websites to
+authenticate users using their Facebook identity~\cite{fb_connect}.  Because it
+is against the terms of service to have multiple Facebook accounts, using
+Facebook Connect has the unwanted side-effect of linking multiple contextual
+identities across multiple sites.
 
@@
 especially for users who don't distinguish the web application from the
-browser, from the operating system, or from the device.
+browser, from the operating system, or from the device\footnote{What is a browser?
+\url{https://www.youtube.com/watch?v=o4MwTvtyrUQ}} \footnote{\url{http://input.mozilla.org/en-US/?q=facebook&product=firefox}}.
 
@@
 \item How is identity represented online?
-\item Is your identity tied to the device you are using?
+\item What do you need to represent your identity?
+\item Is your identity tied to your device?
 \item If you check your mail, read news, log on to a social network at a
@@
 your housemates, friends, relatives, or employers?
+\item Which parts of your online identity do you expect to be visible to
+websites you use? What about websites you don't use?
 \item Which parts of your identity do you want to share with whom?
@@
 
-danah boyd has done excellent work surveying youth and social networks, and Pew
+danah boyd's work surveying youth and social networks is excellent, and Pew
 Internet is a good source for self-reported phone surveys on privacy and social
@@
 areas~\cite{boyd,pew1,pew2,pew3}.
+% digital natives is related but not exactly
 
@@
 identity management techniques.
+
+\subsubsection{Separating identities}
+
+The following examples illustrate how users keep their identities separate.
 
@@
 networks~\cite{twitter}.
-\begin{comment}
-That is not to say that all users have the same
-tolerance or even need for multiple explicit identities: in fact many users may
-be exclusively task-oriented and use the Internet with specific tasks in mind
-rather than for social interaction or exploratory surfing\footnote{Even these
-users are subject to building implicit identities through the use of tracking
-techniques, however.}.
-\end{comment}
 
-\paragraph{Auditing}
-Wang et.~al suggest that common techniques for handling regret online include
-manual deletion of regrettable posts, self-censoring or delaying
-posts that they predict might bring regret~\cite{wang}.
+\paragraph{Multiple browsers}
+
+Using multiple browsers is a useful technique for managing multiple accounts.
+Some services support multiple accounts but not multiple login (e.g.,
+Twitter). For services that do (e.g., many Google services), the user interface
+may be so confusing that it leads to errors, so the best recommendation may be
+to use multiple browsers~\cite{yegge}.\footnote{Google recommends multiple
+browsers as an alternative to multiple login:
+\url{https://support.google.com/accounts/bin/answer.py?hl=en&answer=179235}}.
+Additionally, for users who want to separate work and
+personal browsing, using multiple browsers is the easiest solution.
+
+\paragraph{Multiple devices}
+
+Many users have multiple devices and many use them for different purposes.
+Sometimes the difference in purpose is due to the nature of the device (e.g.,
+GPS and mapping software are probably more often used in mobile devices) and
+some may be due to policy (e.g., personal browsing is limited to a personal
+laptop). Using multiple devices implicitly creates multiple browser states and
+thus multiple identities.  However, these identities may still be linked
+through authentication data or other techniques~\cite{aol}.
+
+\paragraph{Multiple profiles}
+
+Using multiple browsers forces separation between cookies, history, builtin
+password managers, and other local storage. However, several browsers support
+separation of profile data natively. Firefox has a Profile Manager, but it is
+so unusable that it will be removed.\footnote{See
+\url{https://bugzilla.mozilla.org/show\_bug.cgi?id=214675\#c53}.} Google Chrome
+supports multiple profiles\footnote{Manage multiple users on Chrome:
+\url{https://support.google.com/chrome/bin/answer.py?hl=en&answer=2364824}}. In
+both cases, the threat model does not include users with malicious intent in
+the same household.
 
@@
 solution~\cite{ABBJ10}. There is no standard behavior for private browsing
-mode, and interaction with extensions, treatment of cookies, history, and
-bookmarks upon entering and exiting this mode are different and serve different
-use cases. For example, entering private browsing in Firefox does not clear
+mode: interaction with extensions, treatment of cookies, history, and
+bookmarks upon entering and exiting are different across browsers.
+For example, entering private browsing in Firefox does not clear
 cookies, history, or other session data; session data is cleared on exiting
@@
 may be preferable as a ``Guest mode'' where the device owner does not want the
-guest to either view or pollute existing state.
-
-\paragraph{Profile management}
-Although a user may subconsciously be aware of their contextual identities,
-expecting users to enumerate their identities and manually curate them is
-probably too burdensome. Firefox has a Profile Manager, but it is so unusable
-that it will be removed.\footnote{See
-\url{https://bugzilla.mozilla.org/show\_bug.cgi?id=214675\#c53}.}
+guest to either view or pollute existing state. L
 
@@
 service providers like Google and Facebook unless users explicitly choose to
-interact with that site~\cite{disconnect,franzi}.
+interact with that site~\cite{disconnect,franzi}.  Collusion is a tool for
+visualizing cookies~\cite{collusion}, in particular third-party cookies set by
+tracking sites which are typically ad networks.  Once the user knows which
+sites are tracking them, they can choose to block cookies from those sites.
+
+\paragraph{Controlling Information Flow}
+Do Not Track is an HTTP request header that signals to the website that the
+user does not want to be tracked~\cite{dnt}. Although Do Not Track is
+unenforceable from the client side, service providers who ignore signal
+lose reputation by acting against their users' explicit wishes.
+
+\paragraph{Service settings} Service configurations such as Facebook friends,
+Google circles and privacy settings are intended for users to self-manage
+privacy and identity. However, shifting privacy settings and complex,
+interacting features make these configurations unpredictable for many users.
+
+\subsubsection{Linking identities}
+\paragraph{Linking between profiles}
+
+-link from fb profile to blog
+-link between services
+
+\paragraph{Synchronizing browser data}
+
+- Chrome sync
+- picl
+- xmarks
 
@@
 \paragraph{Mitigating explicit linkage}
-Another partial solution is to prompt the user when they're about to link
-multiple contextual identities through a federated login service. For example,
-Persona is the suite of tools that implements the BrowserID protocol, and it
-supports multiple email identifiers~\cite{browserid}.
-Because we can categorize the type of service by URL
-as \texttt{about:profile} does, Persona could prompt the user when they're about
-to link the same email identifier to radically different contextual identities,
-such as ones for dating and professional use.
-
-\paragraph{Controlling Information Flow}
-Do Not Track is an HTTP request header that signals to the website that the
-user does not want to be tracked~\cite{dnt}. Although Do Not Track is
-unenforceable from the client side, service providers who ignore signal will
-lose reputation by acting against their users' explicit wishes.
+Federated login services can prevent linking contextual identities to the same
+user identifier. For example, Persona is the suite of tools that implements the
+BrowserID protocol, and it supports multiple email
+identifiers~\cite{browserid}.  If the type of service is known, Persona could
+prevent the user from associating the same email identifier to radically
+different contextual identities, such as ones for dating and professional use.
 
 \paragraph{Auditing}
+(needs rewrite)
 A major cause of user embarrassment is exposing information to the wrong
@@
 particularly problematic content.
-
-\paragraph{Implicit identity generation}
-Profiles can be generated by user-supplied application-level data, but also
-implicitly through browsing via tracking techniques.  Collusion is a tool for
-visualizing cookies~\cite{collusion}, in particular third-party cookies set by
-tracking sites which are typically ad networks.  Once the user knows which
-sites are tracking them, they can choose to block cookies from those sites.
 

### 2013-03-03 paper.tex
never-ending rewrites

@@
 identities are linked without user intent, or when the user cannot choose which
-contextual identity to assert in a given situation. In these examples the user
+identity to assert in a given context. In these examples the user
 may not be conscious of what a contextual identity is: nevertheless each
@@
 policy, which requires users to register for accounts with their legal
-name~\cite{fb_names,google_names}.  These policies ignore that
+name\footnote{Facebook's policy: \url{http://www.facebook.com/help/?page=258984010787183}, Google's policy: \url{http://support.google.com/plus/bin/answer.py?hl=en&answer=1228271}}.
+%\cite{fb_names,google_names}.  
+These policies ignore that
 community-building happens in many different contexts, that users have many
@@
 example, disallowing avatar handles as a primary identifier makes building a
-gaming community difficult.  Linking a gaming identity to a professional
-identity has already caused problems for 2012 Maine Senate candidate and World
-of Warcraft gamer Colleen Lachowicz~\cite{maine}.
-
-It is impossible for users who want to isolate multiple contextual identities
-to participate in these networks without violating the terms of service.  The
-``Real Names'' policy prohibits users from asserting control over their
-identity.
+gaming community difficult. % Linking a gaming identity to a professional
+%identity has already caused problems for 2012 Maine Senate candidate and World
+%of Warcraft gamer Colleen Lachowicz~\cite{maine}.
+It is impossible to isolate multiple contextual identities in these networks
+without violating the terms of service.
 
@@
 is against the terms of service to have multiple Facebook accounts, using
-Facebook Connect has the unwanted side-effect of linking multiple contextual
-identities across multiple sites.
+Facebook Connect may have the unwanted side-effect of linking multiple
+contextual identities across multiple sites.
 
@@
 \section{Research directions}
-We propose new research directions based on the following questions.
+We propose new research directions based on the following questions:
 \begin{itemize}
@@
 websites you use? What about websites you don't use?
-\item Which parts of your identity do you want to share with whom?
-\item Which parts of your identity do you want to keep secret from whom?
+\item Which parts of your identity do you want to share or keep secret, and from whom?
 \item How does your identity change over time?
@@
 
-danah boyd's work surveying youth and social networks is excellent, and Pew
-Internet is a good source for self-reported phone surveys on privacy and social
-media, but there is otherwise a dearth of research in these
-areas~\cite{boyd,pew1,pew2,pew3}.
-% digital natives is related but not exactly
+Pew Internet is a good source for phone survey data on privacy and social
+media and danah boyd's work on youth and social media is excellent, but there
+is otherwise a dearth of research in these areas~\cite{boyd,pew1,pew2,pew3}.
 
@@
 Users who are aware of having multiple identities engage in the following
-identity management techniques.
+techniques to separate, link, and curate identities.
 
@@
 thus multiple identities.  However, these identities may still be linked
-through authentication data or other techniques~\cite{aol}.
+through authentication data or other techniques.%~\cite{aol}
 
@@
 
-Using multiple browsers forces separation between cookies, history, builtin
+Using multiple browsers forces separation between cookies, history, built-in
 password managers, and other local storage. However, several browsers support
-separation of profile data natively. Firefox has a Profile Manager, but it is
-so unusable that it will be removed.\footnote{See
-\url{https://bugzilla.mozilla.org/show\_bug.cgi?id=214675\#c53}.} Google Chrome
-supports multiple profiles\footnote{Manage multiple users on Chrome:
-\url{https://support.google.com/chrome/bin/answer.py?hl=en&answer=2364824}}. In
-both cases, the threat model does not include users with malicious intent in
+separation of profile data natively. Firefox 
+%\url{https://bugzilla.mozilla.org/show\_bug.cgi?id=214675\#c53}.}
+and Chrome support multiple profiles, though neither of these is very
+discoverable or easy to use.\footnote{Chrome: \url{https://support.google.com/chrome/bin/answer.py?hl=en&answer=2364824}, Firefox:
+\url{https://bugzilla.mozilla.org/show\_bug.cgi?id=214675\#c53}}
+The threat model does not include users with malicious intent in
 the same household.
@@
 \paragraph{Private browsing mode}
-Private browsing mode exists in all major browsers, but are not a complete
-solution~\cite{ABBJ10}. There is no standard behavior for private browsing
-mode: interaction with extensions, treatment of cookies, history, and
+Private browsing mode exists in all major browsers, but has no standard
+behavior~\cite{ABBJ10}.
+Interaction with extensions, treatment of cookies, history, and
 bookmarks upon entering and exiting are different across browsers.
+\begin{comment}
 For example, entering private browsing in Firefox does not clear
@@
 may be preferable as a ``Guest mode'' where the device owner does not want the
-guest to either view or pollute existing state. L
+guest to either view or pollute existing state.
+\end{comment}
+Similar to multiple profiles, private browsing mode is not secure against local
+attacks.
 
@@
 
-\paragraph{Controlling Information Flow}
-Do Not Track is an HTTP request header that signals to the website that the
-user does not want to be tracked~\cite{dnt}. Although Do Not Track is
-unenforceable from the client side, service providers who ignore signal
-lose reputation by acting against their users' explicit wishes.
+\subsubsection{Linking identities}
 
-\paragraph{Service settings} Service configurations such as Facebook friends,
-Google circles and privacy settings are intended for users to self-manage
-privacy and identity. However, shifting privacy settings and complex,
-interacting features make these configurations unpredictable for many users.
+For many users, the natural separation that occurs when creating multiple
+accounts, using multiple browsers and devices is a drawback, not a benefit.
+These users want fewer contextual identities and use the following techniques
+to merge them.
 
-\subsubsection{Linking identities}
 \paragraph{Linking between profiles}
@@
 
+\subsubsection{Curating identities}
+
+\paragraph{Service settings} Service configurations such as Facebook friends,
+Google circles and privacy settings are intended for users to self-manage
+privacy and identity. However, shifting privacy settings and complex,
+interacting features make these configurations unpredictable for many users.
+
+\paragraph{Auditing} Wang et. al suggest that common techniques
+for handling regret online include manual deletion of regret-
+table posts, self-censoring or delaying posts that they predict
+might bring regret~\cite{wang}. Pew Internet reports that 57\% of Internet
+users periodically search for themselves to manage reputation, with young
+adults being the most active~\cite{pew3}.
+
 \subsection{How can we improve identity management tools?}
-\paragraph{Task inference}
-If users' contextual identities are primarily task-oriented, it may be
-possible to infer tasks from the user's activity. For example, the
-\texttt{about:profile} Firefox extension uses the Open Directory Project and
-Alexa to categorize URLs that the user has visited~\cite{aboutprofile}.
 
-\paragraph{Relationship inference}
+Service providers are highly incentivized to make linking identities easy, so
+we concentrate on tools to help separate and curate identities.
+
+\begin{comment}
+\paragraph{Automatically inferring identities}
+A contextual identity may be based on tasks and relationships.
+Browsing activity is a rich source of information for inferring tasks.  For
+example, the \texttt{about:profile} Firefox extension uses the Open Directory
+Project and Alexa to categorize URLs that the user has
+visited~\cite{aboutprofile}.
+
 Tang et al.~show that most people do not take the time to create labels and
@@
 both shoulder-surfing and distraction.
+\end{comment}
 
-\paragraph{Mitigating explicit linkage}
-Federated login services can prevent linking contextual identities to the same
-user identifier. For example, Persona is the suite of tools that implements the
-BrowserID protocol, and it supports multiple email
-identifiers~\cite{browserid}.  If the type of service is known, Persona could
-prevent the user from associating the same email identifier to radically
-different contextual identities, such as ones for dating and professional use.
+\paragraph{Mitigating explicit linkage} Federated login services can prevent
+linking contextual identities to the same user identifier.  For example, a
+federated login service that supported multiple identifiers could prevent the
+user from associating the same identifier to radically different
+contextual identities, such as ones for dating and professional use.
 
 \paragraph{Auditing}
-(needs rewrite)
-A major cause of user embarrassment is exposing information to the wrong
-audience. A browser is in an ideal position to intermediate social network
+A browser is in an ideal position to intermediate social network
 posts, aggregate them locally, and present them to the user when they desire to
@@
 comments and posts they made in the last week and redact content that is
-sensitive or too negative, a frequent cause of regret~\cite{wang}.  Although
-this approach does not help when the service provider decides to change the
-audience on the user's behalf, auditing gives the user a good opportunity to
-review posts that might cause regrets. In the case of high-volume users, such a
-tool could incorporate sentiment analysis to aid the user in finding
+sensitive or too negative, a frequent cause of regret~\cite{wang}. 
+Such a tool could incorporate sentiment analysis to aid the user in finding
 particularly problematic content.
 
-\paragraph{Visual reminders of context}
-To mitigate privacy violations caused by poor user interfaces, the software
-must provide sufficient visual cues of context. For example, many but not all
-Google products support multiple accounts. However, the visual cue to indicate
-which account is active is a small, easy to ignore text name at the top right
-of the page.
-
 \paragraph{Expiring posts}
-Humans don't have perfect memories, and perhaps social networks should not
-either~\cite{delete}. Many users already engage in manual auditing and deletion
+Humans don't have perfect memories, so perhaps social networks shouldn't either
+~\cite{delete}. Many users already engage in manual auditing and deletion
 of old posts~\cite{fbtips2}. A better solution would be to build tools that let
 the user manage this more easily through an API: both Twitter and Facebook
-provide APIs for post deletion\footnote{Google Plus
-offers a read-only API.}. One way to reduce the likelihood of linked contextual
-identities would be to provide applications that expire posts after some time.
+provide APIs for post deletion\footnote{Google Plus offers a read-only API.}.
 
@@
 outlived their usefulness, users would benefit from destruction of side-effects
-such as cookie data.
+such as cookie data and service accounts.
 

### 2013-03-04 paper.tex
rewrites may be ending soon?

@@
 considered as a proxy for identity if tied to service accounts. Similarly, data
-suggests that a large minority of Twitter users have multiple Twitter accounts,
-and the plethora of cross-posting or syndication software from one social
-network to another suggests that many users take advantage of multiple social
-networks~\cite{twitter}.
+suggests that a large minority of Twitter users have multiple Twitter
+accounts~\cite{twitter}.
 
@@
 
-\paragraph{Linking between profiles}
+\paragraph{Building social graphs}
 
--link from fb profile to blog
--link between services
+Users can explicitly create links between contextual identities, e.g.  linking
+to their blog from their Flickr profile, or resharing a blog post via Twitter.
+It is also easy to implicitly create links between contextual identities,
+sometimes accidentally: generating two isomorphic graphs at different services
+is often enough to re-identify an individual~\cite{narayanan1}. The plethora of
+cross-posting software available suggests that users often want to link
+identities.
+
+Building reputation online is a long and arduous process; a user who has built
+up high credibility in one social network may want to transfer that credibility
+when using a new service by using the same identifier or somehow proving in the
+new service that they control other existing, credible identities.  The rise of
+verified account mechanisms in Twitter, Google Plus and Facebook indicates that
+this is a real problem.
 
@@
 
-- Chrome sync
-- picl
-- xmarks
+All five major browsers (Firefox, Chrome, Safari, Internet Explorer, and Opera)
+offer synchronizing some set of browser data across devices, with varying
+degrees of success. Multiple cross-browser applications also exist to
+synchronize bookmarks and passwords~\footnote{Bookmark sync: \url{xmarks.com}, password sync: \url{lastpass.com}}.
 
 \subsubsection{Curating identities}
+
+Given the large number of social network users and that 30-40\% of spoken
+communication is devoted to informing others about ourselves, many users are
+bound to share personal information online that they regret~\cite{tamir}.
 
@@
 \paragraph{Auditing} Wang et. al suggest that common techniques
-for handling regret online include manual deletion of regret-
-table posts, self-censoring or delaying posts that they predict
-might bring regret~\cite{wang}. Pew Internet reports that 57\% of Internet
-users periodically search for themselves to manage reputation, with young
-adults being the most active~\cite{pew3}.
+for handling regret online include manual deletion of regret- table posts,
+self-censoring or delaying posts that they predict might bring
+regret~\cite{wang}. Pew Internet reports that 57\% of Internet users
+periodically search for themselves to manage reputation, with young adults
+being the most active~\cite{pew3}.
 
@@
 
-Service providers are highly incentivized to make linking identities easy, so
-we concentrate on tools to help separate and curate identities.
+Service providers are highly incentivized to make linking identities easy;
+more tools to help separate and curate identities are necessary. Without
+knowing more about how users think about identity, we concentrate solely on
+automating manual processes that users already perform.
 
@@
 
-\paragraph{Mitigating explicit linkage} Federated login services can prevent
+\paragraph{Mitigating accidental linkage} Federated login services can prevent
 linking contextual identities to the same user identifier. For example, a
@@
 \paragraph{Expiring posts}
-Humans don't have perfect memories, so perhaps social networks shouldn't either
-~\cite{delete}. Many users already engage in manual auditing and deletion
-of old posts~\cite{fbtips2}. A better solution would be to build tools that let
-the user manage this more easily through an API: both Twitter and Facebook
-provide APIs for post deletion\footnote{Google Plus offers a read-only API.}.
+Humans don't have perfect memories, and neither should social
+networks~\cite{delete}. Many users already engage in manual auditing and
+deletion of old posts~\cite{fbtips2}. A better solution would be to build tools
+that let the user manage this more easily through an API: both Twitter and
+Facebook provide APIs for post deletion\footnote{Google Plus offers a read-only
+API.}.
 
 \paragraph{Expiring contextual identities}
-Engaging in a long-term task such as house-buying
-often requires the construction of a contextual identity. The tasks associated
-with this identity have an externally imposed end date and may have long-lived
-side-effects, such as long-term cookies that reveal sensitive information
-(e.g., the neighborhood of the house purchase, income information derived from
-purchases, other demographic data). For contextual identities that have
-outlived their usefulness, users would benefit from destruction of side-effects
-such as cookie data and service accounts.
+Engaging in a long-term task such as house-buying often requires the
+construction of a contextual identity. The tasks associated with this identity
+have an externally imposed end date and may have long-lived side-effects, such
+as long-term cookies that reveal sensitive information (e.g., the neighborhood
+of the house purchase, income information derived from purchases, other
+demographic data). For contextual identities that have outlived their
+usefulness, users would benefit from destruction of side-effects such as cookie
+data and service accounts.
 
@@
 appropriate contexts fosters positive human interaction.  We hope that
-contextual identity will serve as a useful notion for developers to understand
-their users' privacy needs, and to develop tools that allow users to act in
-their contextual identities in a spontaneous, relaxed, and interesting way.
+contextual identity serves as a useful notion for developers to understand
+their users' privacy needs and develop tools to help users manage their
+identities.
 

### 2013-03-04 paper.tex
Clean up punctuation, delete unnecessary words

@@
 We examine \textit{contextual identity}, a notion that individuals reveal
-different aspects of themselves depending on context. At any given time, they
-may act as a friend, relative, spouse, co-worker, aquaintance, or stranger. We
-analyze contextual identity from the perspective of user choice and control,
-survey contextual identity violations, and propose new resesarch directions to
-empower users to have better control over their contextual identities.
+different aspects of themselves depending on context. At any given time,
+an individual may act as a friend, relative, spouse, co-worker, aquaintance, or
+stranger. We analyze contextual identity from the perspective of user choice
+and control, survey contextual identity violations, and propose new resesarch
+directions to enable users to have better control over their contextual
+identities.
 \end{abstract}
@@
 simple sharing of personal information, but rather from sharing that
-information in a way that violates social norms, or in the wrong
-context~\cite{nissenbaum}.
+information in a way that violates social norms~\cite{nissenbaum}.
 
@@
 identity violations.  Access to support is crucial for LGTB-identified youth,
-who are at higher risk for bullying and suicide than non-LGTB youth~\cite{hrc}.
+who are at higher risk for bullying and suicide~\cite{hrc}.
 Much of that support is only accessible through the Internet in socially
@@
 
-Barth, Datta, Mitchell, and Nissenbaum provide a formal model for contextual
-integrity of user data~\cite{barth}. The contextual integrity model focuses on
+Barth et al.~provide a formal model for contextual
+integrity of user data~\cite{barth}. Their work models
 the flow of personal information in terms of knowledge states held by agents
-acting in given roles, and works well for modeling privacy legislation such as
+acting in given roles, and works well for expressing privacy legislation such as
 HIPPA and COPPA. Two limitations of this work are that it does not
@@
 \subsection{Redistributing information out of context}
-Re-distributing information out of its original context often leads to
+Redistributing information out of its original context often leads to
 embarrassment~\cite{nissenbaum}.  In November 2007, Facebook Beacon allowed
@@
 policy, which requires users to register for accounts with their legal
-name\footnote{Facebook's policy: \url{http://www.facebook.com/help/?page=258984010787183}, Google's policy: \url{http://support.google.com/plus/bin/answer.py?hl=en&answer=1228271}}.
+name.\footnote{Facebook's policy: \url{http://www.facebook.com/help/?page=258984010787183}, Google's policy: \url{http://support.google.com/plus/bin/answer.py?hl=en&answer=1228271}}
 %\cite{fb_names,google_names}.  
 These policies ignore that
-community-building happens in many different contexts, that users have many
+community-building happens in many different contexts, that users have
 legitimate reasons for presenting different identities in different contexts,
@@
 Some login platforms and protocols, such as OAuth and BrowserID, do not suffer
-from this policy or design error~\cite{browserid,oauth}, giving a user better
-control over which contextual identity to assert.
+from this policy or design error, giving a user better
+control over which contextual identity to assert~\cite{browserid,oauth}.
 
@@
 mistyping a single character (\texttt{@} instead of \texttt{d}), it's no
-surprise that DM failures are exceedingly common.
+surprise that DM failures are so common.
 
@@
 understand users' mental models of identity and how information is shared on
-the Internet. For computer scientists, authentication is tied to identity, and
-even in the absence of authentication, using the same device over time
-implicitly creates an identity through tracking techniques and local
+the Internet. For computer scientists, authentication is intrinsically linked
+to identity, and even in the absence of authentication, using the same device
+over time implicitly creates an identity through tracking techniques and local
 information. However, these points are far from obvious to a typical user,
 especially for users who don't distinguish the web application from the
-browser, from the operating system, or from the device\footnote{What is a browser?
-\url{https://www.youtube.com/watch?v=o4MwTvtyrUQ}} \footnote{\url{http://input.mozilla.org/en-US/?q=facebook&product=firefox}}.
+browser, from the operating system, or from the device.\footnote{What is a
+browser? \url{https://www.youtube.com/watch?v=o4MwTvtyrUQ}}
 
@@
 notions of identity if we are to help users to whom the very concept of
-identity is an enigma. To start understanding our users' mental models,
-one might start with the questions:
+identity is an enigma. To understand our users' mental models,
+one might ask:
 
@@
 Pew Internet is a good source for phone survey data on privacy and social
-media and danah boyd's work on youth and social media is excellent, but there
+media, and danah boyd's work on youth and social media is excellent, but there
 is otherwise a dearth of research in these areas~\cite{boyd,pew1,pew2,pew3}.
@@
 may be so confusing that it leads to errors, so the best recommendation may be
-to use multiple browsers~\cite{yegge}.\footnote{Google recommends multiple
+to use multiple browsers~\cite{yegge}.\footnote{Using multiple
 browsers as an alternative to multiple login:
-\url{https://support.google.com/accounts/bin/answer.py?hl=en&answer=179235}}.
-Additionally, for users who want to separate work and
+\url{https://support.google.com/accounts/bin/answer.py?hl=en&answer=179235}}
+For users who want to separate work and
 personal browsing, using multiple browsers is the easiest solution.
@@
 
-Using multiple browsers forces separation between cookies, history, built-in
-password managers, and other local storage. However, several browsers support
-separation of profile data natively. Firefox 
+Several browsers support separation of profile data, including cookies,
+history, passwords, and other local storage. Firefox 
 %\url{https://bugzilla.mozilla.org/show\_bug.cgi?id=214675\#c53}.}
 and Chrome support multiple profiles, though neither of these is very
-discoverable or easy to use.\footnote{Chrome: \url{https://support.google.com/chrome/bin/answer.py?hl=en&answer=2364824}, Firefox:
-\url{https://bugzilla.mozilla.org/show\_bug.cgi?id=214675\#c53}}
-The threat model does not include users with malicious intent in
-the same household.
+discoverable or easy to use.\footnote{Chrome:
+\url{https://support.google.com/chrome/bin/answer.py?hl=en&answer=2364824},
+Firefox: \url{https://bugzilla.mozilla.org/show\_bug.cgi?id=214675\#c53}} The
+threat model does not include users with malicious intent in the same
+household.
 
@@
 bookmarks upon entering and exiting are different across browsers.
-\begin{comment}
-For example, entering private browsing in Firefox does not clear
-cookies, history, or other session data; session data is cleared on exiting
-private browsing mode. In contrast, incognito mode in Chrome makes previous
-session state unavailable and clears new session state on exit; this mode
-may be preferable as a ``Guest mode'' where the device owner does not want the
-guest to either view or pollute existing state.
-\end{comment}
 Similar to multiple profiles, private browsing mode is not secure against local
@@
 interact with that site~\cite{disconnect,franzi}.  Collusion is a tool for
-visualizing cookies~\cite{collusion}, in particular third-party cookies set by
-tracking sites which are typically ad networks.  Once the user knows which
-sites are tracking them, they can choose to block cookies from those sites.
+visualizing and blocking cookies~\cite{collusion}, in particular third-party
+cookies set by tracking sites which are typically ad networks.
 
@@
 when using a new service by using the same identifier or somehow proving in the
-new service that they control other existing, credible identities.  The rise of
-verified account mechanisms in Twitter, Google Plus and Facebook indicates that
-this is a real problem.
+new service that they control other credible identities.  The advent
+of verified account mechanisms in Twitter, Google Plus and Facebook indicates
+that this problem is on the rise.
 
@@
 degrees of success. Multiple cross-browser applications also exist to
-synchronize bookmarks and passwords~\footnote{Bookmark sync: \url{xmarks.com}, password sync: \url{lastpass.com}}.
+synchronize bookmarks and passwords.\footnote{Bookmark sync: \url{xmarks.com}, password sync: \url{lastpass.com}}
 
@@
 communication is devoted to informing others about ourselves, many users are
-bound to share personal information online that they regret~\cite{tamir}.
+bound to share information they later regret~\cite{tamir}.
 
@@
 automating manual processes that users already perform.
-
-\begin{comment}
-\paragraph{Automatically inferring identities}
-A contextual identity may be based on tasks and relationships.
-Browsing activity is a rich source of information for inferring tasks.  For
-example, the \texttt{about:profile} Firefox extension uses the Open Directory
-Project and Alexa to categorize URLs that the user has
-visited~\cite{aboutprofile}.
-
-Tang et al.~show that most people do not take the time to create labels and
-maintain friend lists~\cite{tang}. However, the same authors show how to use
-heterogeneous networks to infer relationship types (e.g., manager-subordinate)
-though the graph itself is unlabeled.
-
-\paragraph{Mitigating implicit linkage}
-Given a user's contextual identities, we may be able to prevent information
-leakage between them.  For example, preventing third-party cookies from being
-read and set across task boundaries means that targeted ads for dating would
-not follow the user when visiting a technology news site. Knowing the user's
-current contextual identity also allows the browser to suppress URL bar
-suggestions that aren't relevant to that identity, protecting the user from
-both shoulder-surfing and distraction.
-\end{comment}
 
@@
 that let the user manage this more easily through an API: both Twitter and
-Facebook provide APIs for post deletion\footnote{Google Plus offers a read-only
-API.}.
+Facebook provide APIs for post deletion.
+%\footnote{Google Plus offers a read-only API.}
 

### 2013-03-06 paper.tex
check connective tissue

@@
 third-party sites to publish purchases, travel bookings, movie rentals and more
-to the user's activity stream.  Because of poor opt-out and lack of visibility
-into what was being published, user outcry was
-immediate~\cite{mccarthy,nakashima}.  In December 2007, Google Reader exposed
+to the user's activity stream.  Poor opt-out and lack of visibility
+into what was being published led to user surprise and dismay~\cite{mccarthy,nakashima}.  In December 2007, Google Reader exposed
 RSS feeds of user-marked news stories to the user's Google Talk contacts, which
@@
 
-The following examples illustrate how users keep their identities separate.
+The following examples illustrate how users attempt to preserve boundaries
+between identities. None of these techniques are failsafe, but they serve as
+useful reminders that perfect solutions may not be necessary, especially in the
+case where information leaks by casual or accidental inspection.
 
@@
 Some services support multiple accounts but not multiple login (e.g.,
-Twitter). For services that do (e.g., many Google services), the user interface
+Twitter). For services that do, the user interface
 may be so confusing that it leads to errors, so the best recommendation may be
@@
 Many users have multiple devices and many use them for different purposes.
-Sometimes the difference in purpose is due to the nature of the device (e.g.,
+Some of this difference is due to the nature of the device (e.g.,
 GPS and mapping software are probably more often used in mobile devices) and
-some may be due to policy (e.g., personal browsing is limited to a personal
+some may be due to policy (e.g., limiting work activities to a corporate
 laptop). Using multiple devices implicitly creates multiple browser states and
@@
 %\url{https://bugzilla.mozilla.org/show\_bug.cgi?id=214675\#c53}.}
-and Chrome support multiple profiles, though neither of these is very
-discoverable or easy to use.\footnote{Chrome:
+and Chrome support multiple profiles, though neither of these implementations
+is discoverable or easy to use.\footnote{Chrome:
 \url{https://support.google.com/chrome/bin/answer.py?hl=en&answer=2364824},
@@
 is often enough to re-identify an individual~\cite{narayanan1}. The plethora of
-cross-posting software available suggests that users often want to link
+cross-posting software suggests that users often want to link
 identities.
@@
 new service that they control other credible identities.  The advent
-of verified account mechanisms in Twitter, Google Plus and Facebook indicates
-that this problem is on the rise.
+of verified account mechanisms in Twitter, Google Plus and Facebook suggests
+this problem is on the rise.
 
@@
 All five major browsers (Firefox, Chrome, Safari, Internet Explorer, and Opera)
-offer synchronizing some set of browser data across devices, with varying
-degrees of success. Multiple cross-browser applications also exist to
-synchronize bookmarks and passwords.\footnote{Bookmark sync: \url{xmarks.com}, password sync: \url{lastpass.com}}
+offer synchronizing a subset of browser data across devices.
+Multiple cross-browser applications also exist to
+synchronize bookmarks and passwords.\footnote{An example of bookmark sync is \url{xmarks.com}, one cloud-based password manager is \url{lastpass.com}.}
 
@@
 interacting features make these configurations unpredictable for many users.
+According to Pew Internet, 71\% of users change privacy-related settings; yet
+the large number of users who experience regret on social networks indicates
+that these settings are not working as intended~\cite{pew3}.
 
@@
 Service providers are highly incentivized to make linking identities easy;
-more tools to help separate and curate identities are necessary. Without
+users need more tools to help separate and curate identities. Without
 knowing more about how users think about identity, we concentrate solely on
@@
 \paragraph{Expiring posts}
-Humans don't have perfect memories, and neither should social
-networks~\cite{delete}. Many users already engage in manual auditing and
+Humans don't have perfect memories, and we question why social networks
+do~\cite{delete}. Many users already engage in manual auditing and
 deletion of old posts~\cite{fbtips2}. A better solution would be to build tools
@@
 People have multiple contextual identities. Sharing personal information in
-appropriate contexts fosters positive human interaction.  We hope that
+appropriate contexts fosters positive human interaction and doesn't negate the need or desire for privacy. We hope that
 contextual identity serves as a useful notion for developers to understand

### 2013-03-06 paper.tex
tiny fix, based on elastic self

@@
 between identities. None of these techniques are failsafe, but they serve as
-useful reminders that perfect solutions may not be necessary, especially in the
-case where information leaks by casual or accidental inspection.
+useful reminders that perfect solutions may not be necessary or even desirable,
+especially in the case where information leaks by casual or accidental
+inspection.
 

### 2013-03-06 paper.tex
translated overuse of 'user', and some minor edits

@@
 identity violations.  Access to support is crucial for LGTB-identified youth,
-who are at higher risk for bullying and suicide~\cite{hrc}.
-Much of that support is only accessible through the Internet in socially
+who are at higher risk for bullying and suicide~\cite{hrc}, though
+much of that support is only accessible through the Internet in socially
 conservative areas. In 2011 Bobbi Duncan and Taylor McCormick, two
@@
 Chorus~\cite{fowler}. Even though both students had blocked their parents from
-seeing any personal posts revealing their sexuality, because Queer Chorus is a
-public group Facebook published notifications to Duncan's and McCormick's
+seeing any personal posts revealing their sexuality, Queer Chorus is a
+public group and so Facebook published notifications to Duncan's and McCormick's
 friends, including their parents. Duncan later attempted suicide~\cite{duncan}.
@@
 
-In offline environments, managing contextual identities is more intuitive than
-in online environments. There are cues to help you determine where you are,
+Managing contextual identities is more intuitive in offline environments than
+in online environments. Offline, there are cues to help you determine where you are,
 who your intended audience is, how many people will overhear you, and how
@@
 Many authors have noted how re-broadcasting information information out of
-context and making information discoverable can lead to user distress, even if
+context and making information discoverable can lead to distress, even if
 the information was previously public, but not easily
@@
 
-Evidence suggests that users' major privacy concerns come from people the user
+Evidence suggests that a person's major privacy concerns come from others he or she
 knows: friends, family, and co-workers~\cite{fbtips2,fbtips1}.  Surveys
 conducted by Wang et al.~suggest that typical regrets from posting on Facebook
-stem almost exclusively from fear of negative interactions with people that the
-user knows~\cite{wang}. The consequences of these negative interactions can
+stem almost {\em exclusively} from fear of negative interactions with people the individual knows~\cite{wang}. The consequences of these negative interactions can
 lead to loss of employment or breaking personal relationships.  Most previous
@@
 behavioral tracking service, state agent or unknown eavesdropper; in contrast,
-we assert that users care more about their interactions with others close to
+we assert that people care more about their interactions with others close to
 them.
@@
 violations}. We consider a contextual identity violation to be when multiple
-identities are linked without user intent, or when the user cannot choose which
-identity to assert in a given context. In these examples the user
+identities are linked without owner intent, or when someone cannot choose which
+identity to assert in a given context. In these examples the individual
 may not be conscious of what a contextual identity is: nevertheless each
-example illustrates a loss of user control over what aspects of self to
+example illustrates a loss of control over what aspects of self to
 reveal in a given context.
@@
 third-party sites to publish purchases, travel bookings, movie rentals and more
-to the user's activity stream.  Poor opt-out and lack of visibility
+to the user's activity stream.  Difficulty of opt-out and lack of visibility
 into what was being published led to user surprise and dismay~\cite{mccarthy,nakashima}.  In December 2007, Google Reader exposed
@@
 Although wall posts were always visible from profile pages, the new Timeline
-interface brought old wall posts, which users used to treat as private messages
+interface brought old wall posts, which people used to treat as private messages
 before the advent of ``Like'' and comment buttons, to the attention of an
-audience that the user never anticipated~\cite{timeline}.
+audience that the posting party never anticipated~\cite{timeline}.
 
@@
 contextual identities. For example, Facebook and Google have a ``Real Names''
-policy, which requires users to register for accounts with their legal
+policy, which requires people to register for accounts with their legal
 name.\footnote{Facebook's policy: \url{http://www.facebook.com/help/?page=258984010787183}, Google's policy: \url{http://support.google.com/plus/bin/answer.py?hl=en&answer=1228271}}
@@
 These policies ignore that
-community-building happens in many different contexts, that users have
+community-building happens in many different contexts, that individuals have
 legitimate reasons for presenting different identities in different contexts,
-and that users don't necessarily want those identities to be linked. For
+and they don't necessarily want those identities to be linked. For
 example, disallowing avatar handles as a primary identifier makes building a
@@
 sites. For example, Facebook Connect allows third-party websites to
-authenticate users using their Facebook identity~\cite{fb_connect}.  Because it
+authenticate individuals using their Facebook identity~\cite{fb_connect}.  Because it
 is against the terms of service to have multiple Facebook accounts, using
@@
 \subsection{How do users think about identity?}
-We hypothesize many users are not consciously aware of having multiple
-contextual identities. In order to develop tools to help users, we need to
-understand users' mental models of identity and how information is shared on
+We hypothesize many people are not consciously aware of having multiple
+contextual identities. In order to develop helpful tools, we need to
+understand people's mental models of identity and how information is shared on
 the Internet. For computer scientists, authentication is intrinsically linked
@@
 over time implicitly creates an identity through tracking techniques and local
-information. However, these points are far from obvious to a typical user,
-especially for users who don't distinguish the web application from the
+information. However, these points are far from obvious to a typical web user,
+especially for those who don't distinguish the web application from the
 browser, from the operating system, or from the device.\footnote{What is a
@@
 notions of identity if we are to help users to whom the very concept of
-identity is an enigma. To understand our users' mental models,
-one might ask:
+identity is an enigma. To understand people's mental models,
+we might ask:
 
@@
 media, and danah boyd's work on youth and social media is excellent, but there
-is otherwise a dearth of research in these areas~\cite{boyd,pew1,pew2,pew3}.
+is otherwise a scarcity of research in these areas~\cite{boyd,pew1,pew2,pew3}.
 
-\subsection{How do users manage identity?}
+\subsection{How do people manage identity?}
 
-Users who are aware of having multiple identities engage in the following
+Those who are aware of having multiple identities engage in the following
 techniques to separate, link, and curate identities.
@@
 
-The following examples illustrate how users attempt to preserve boundaries
+The following examples illustrate how individuals attempt to preserve boundaries
 between identities. None of these techniques are failsafe, but they serve as
@@
 The long-time existence of support for multiple accounts in email clients
-suggests that many users have multiple email identifiers, which could be
+suggests that many people have multiple email identifiers, which could be
 considered as a proxy for identity if tied to service accounts. Similarly, data
@@
 \url{https://support.google.com/accounts/bin/answer.py?hl=en&answer=179235}}
-For users who want to separate work and
+For those who want to separate work and
 personal browsing, using multiple browsers is the easiest solution.
@@
 
-Many users have multiple devices and many use them for different purposes.
+Many people have multiple devices and many use them for different purposes.
 Some of this difference is due to the nature of the device (e.g.,
@@
 bookmarks upon entering and exiting are different across browsers.
-Similar to multiple profiles, private browsing mode is not secure against local
-attacks.
+Similar to multiple profiles, private browsing mode is not generally secure
+against all local attacks.
 
@@
 users need more tools to help separate and curate identities. Without
-knowing more about how users think about identity, we concentrate solely on
+knowing more about how people think about identity, we concentrate solely on
 automating manual processes that users already perform.
@@
 A browser is in an ideal position to intermediate social network
-posts, aggregate them locally, and present them to the user when they desire to
-audit their digital footprint.  For example, a user could see all of the
+posts, aggregate them locally, and present them to its user when she wants to
+audit her digital footprint.  For example, people could inspect all of the
 comments and posts they made in the last week and redact content that is
 sensitive or too negative, a frequent cause of regret~\cite{wang}. 
-Such a tool could incorporate sentiment analysis to aid the user in finding
+Such a tool could incorporate sentiment analysis to aid its user in finding
 particularly problematic content.
@@
 demographic data). For contextual identities that have outlived their
-usefulness, users would benefit from destruction of side-effects such as cookie
+usefulness, people would benefit from destruction of side-effects such as cookie
 data and service accounts.
@@
 \section{Summary}
-People have multiple contextual identities. Sharing personal information in
+People have multiple contextual identities, and often attempt to leverage them differently. Sharing personal information in
 appropriate contexts fosters positive human interaction and doesn't negate the need or desire for privacy. We hope that
 contextual identity serves as a useful notion for developers to understand
-their users' privacy needs and develop tools to help users manage their
-identities.
+their users' privacy needs and seek to understand identity use better so we can develop tools for effective identity management.
 

### 2013-03-06 paper.tex
Change title, clarify incentives to make linking easy

@@
 
-\title{Contextual Identity: Towards Usable Privacy}
+\title{Contextual Identity: Freedom to be all Your Selves}
+%\title{Contextual Identity: All your selves are belong to you}
 
@@
 identity violations.  Access to support is crucial for LGTB-identified youth,
-who are at higher risk for bullying and suicide~\cite{hrc}, though
+who are at higher risk for bullying and suicide~\cite{hrc}, and
 much of that support is only accessible through the Internet in socially
@@
 bookmarks upon entering and exiting are different across browsers.
-Similar to multiple profiles, private browsing mode is not generally secure
+Similar to multiple profiles, private browsing mode is not secure
 against all local attacks.
@@
 
-Service providers are highly incentivized to make linking identities easy;
+Service providers compete for customers by providing a platform that
+meets all of their needs.  The multiplicity of social media means that
+in order to be competitive, social networks encourage cross-linking,
+resharing, and resyndication --- all of which promote linking identities.
+Linking identities is already easy;
 users need more tools to help separate and curate identities. Without

### 2013-03-07 paper.tex
ispell, last read through (probably)

@@
 different aspects of themselves depending on context. At any given time,
-an individual may act as a friend, relative, spouse, co-worker, aquaintance, or
+an individual may act as a friend, relative, spouse, co-worker, acquaintance, or
 stranger. We analyze contextual identity from the perspective of user choice
-and control, survey contextual identity violations, and propose new resesarch
+and control, survey contextual identity violations, and propose new research
 directions to enable users to have better control over their contextual
@@
 conservative areas. In 2011 Bobbi Duncan and Taylor McCormick, two
-students at the University of Texas at Austin, were inadvertantly outed when
+students at the University of Texas at Austin, were inadvertently outed when
 their choir director added them to a Facebook group for Queer
@@
 The following examples illustrate how individuals attempt to preserve boundaries
-between identities. None of these techniques are failsafe, but they serve as
+between identities. None of these techniques are fail-safe, but they serve as
 useful reminders that perfect solutions may not be necessary or even desirable,
@@
 
-\paragraph{Service settings} Service configurations such as Facebook friends,
-Google circles and privacy settings are intended for users to self-manage
-privacy and identity. However, shifting privacy settings and complex,
+\paragraph{Service settings} Features such as Facebook friends,
+Google circles and privacy settings presumably allow users to manage their
+privacy and identity. However, shifting implementations and complex,
 interacting features make these configurations unpredictable for many users.
@@
 
-\paragraph{Auditing} Wang et. al suggest that common techniques
+\paragraph{Auditing} Wang et al.~suggest that common techniques
 for handling regret online include manual deletion of regret- table posts,
@@
 
-Service providers compete for customers by providing a platform that
-meets all of their needs.  The multiplicity of social media means that
+The multiplicity of social media means that
 in order to be competitive, social networks encourage cross-linking,
@@
 sensitive or too negative, a frequent cause of regret~\cite{wang}. 
-Such a tool could incorporate sentiment analysis to aid its user in finding
+Such a tool could incorporate sentiment analysis to find
 particularly problematic content.
@@
 \begin{comment}
-\section{Acknowledgements}
+\section{Acknowledgments}
 The authors thank

### 2013-03-07 paper.tex
adverbs capitalized in title
minor cleanup

@@
 
-\title{Contextual Identity: Freedom to be all Your Selves}
+\title{Contextual Identity: Freedom to be All Your Selves}
 %\title{Contextual Identity: All your selves are belong to you}
@@
 \section{Summary}
-People have multiple contextual identities, and often attempt to leverage them differently. Sharing personal information in
+People have multiple contextual identities for multiple different reasons. Sharing personal information in
 appropriate contexts fosters positive human interaction and doesn't negate the need or desire for privacy. We hope that

### 2013-04-23 paper.tex
minor cleanup
Update based on reviews

@@
 
+Although access control and usability play a role in contextual identity
+management, they are not a panacea: many of the below examples fall out of
+scope of traditional access control models.
+
 \label{sec:examples}
@@
 Those who are aware of having multiple identities engage in the following
-techniques to separate, link, and curate identities.
+techniques to separate, link, and curate identities. These techniques are by no
+means complete or optimal: people may have latent needs that are not met
+by current tools. Studying usage and common problems of these techniques is a
+worthy goal.
 
@@
 \section{Summary}
-People have multiple contextual identities for multiple different reasons. Sharing personal information in
+People have multiple contextual identities for many different reasons. Sharing personal information in
 appropriate contexts fosters positive human interaction and doesn't negate the need or desire for privacy. We hope that

### 2013-04-24 paper.tex
minor cleanups

@@
 The desire for privacy balances the desire for spontaneous, positive human
-interaction, which often requires sharing personal information. The act of
+interaction and sharing personal information. The act of
 sharing alone does not negate expectation of privacy~\cite{boyd2}.
@@
 Helen Nissenbaum has long argued that privacy violations come not from the
-simple sharing of personal information, but rather from sharing that
+simple sharing of personal information itself, but rather from sharing that
 information in a way that violates social norms~\cite{nissenbaum}.
 
-Lesbian, gay, bisexual, and transgendered youth are at risk for contextual
+For example, lesbian, gay, bisexual, and transgendered youth are particularly at risk for contextual
 identity violations.  Access to support is crucial for LGTB-identified youth,
@@
 networks, information is rarely about a single person, and the tone of the
-message is as important to user effect as the contents.
+message is as important to its effect on a user as the contents.
 
@@
 behavioral tracking service, state agent or unknown eavesdropper; in contrast,
-we assert that people care more about their interactions with others close to
+we assert that people are concerned about their interactions with others close to
 them.
@@
 
-Although access control and usability play a role in contextual identity
+Although additional access control and improved usability can improve contextual identity
 management, they are not a panacea: many of the below examples fall out of
@@
 \label{sec:examples}
-\subsection{Redistributing information out of context}
+\subsection{Redistributing information in a different context}
 Redistributing information out of its original context often leads to
@@
 
-\subsection{Policy errors}
+\subsection{Unaccommodating policies}
 \label{sec:policies}
@@
 
-\subsection{User interface errors}
+\subsection{Confusing user interfaces}
 It is all too easy for users to broadcast information to
